---
title: "network_analysis"
author: "Pietro Olivetti"
date: "2024-10-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Network analysis of Depression and Anxiety Symptomatology


## Packages and loading

```{r packages, message=FALSE, warning=FALSE}
library(dplyr)
library(igraph)
library(qgraph)
library(bootnet)
library(corpcor)
library(openxlsx)
library(ggplot2)
library(tidyr)
library(matrixcalc)
library(e1071)
library(networktools)
#library(smacof)
source('../data/questions.R')
```

```{r, message=FALSE, warning=FALSE}
multiC <- function(cor_mat, t_hold = 0.8, name = ""){threshold <- t_hold
high_corr_pairs <- which(abs(cor_mat) > threshold & abs(cor_mat) < 1, arr.ind = TRUE)

# variable names and corresponding correlation values
high_corr_list <- data.frame(
  Variable1 = rownames(cor_mat)[high_corr_pairs[, 1]],
  Variable2 = colnames(cor_mat)[high_corr_pairs[, 2]],
  Correlation = cor_mat[high_corr_pairs]
)

# variables and their correlation values
df <- high_corr_list %>%
  arrange(desc(Correlation))}
```

## Organizing data


### All variables
Creating the dataframe and the group's list for all variables
```{r, message=FALSE, warning=FALSE}

# Dataframe
df <- read.csv('../data/data_cleaned_temp.csv')

# Groups
groups_all_variables <- list(Ids = 1, Sociodem = 2:8, Pers_BFI2 = 9:23, Pers_hexaco = 24:33, Depr_cesd = 34:53, Depr_phq = 54:62, Depr_promis = 63:90, Depr_qids = 91:106, Depr_Ans_dass = 107:120, Depr_Ans_hads = 121:134, Ans_gad = 135:141, Ans_tmas = 142:191, Ans_sas = 192:206)

########
```


### All Scales

Creating the dataframe and the group's list for all scales
```{r, message=FALSE, warning=FALSE}
# Dataframe
df_all_scales <- df[9:206]

groups_all_scales <- list(Pers_BFI2 = 1:15, Pers_hexaco = 16:25, Depr_cesd = 26:45, Depr_phq = 46:54, Depr_promis = 55:82, Depr_qids = 83:98, Depr_Ans_dass = 99:112, Depr_Ans_hads = 113:126, Ans_gad = 127:133, Ans_tmas = 134:183, Ans_sas = 184:198)

group_names <- c("Ids", "Sociodem", "Pers_BFI2", "Pers_hexaco", "Depr_cesd", "Depr_phq", "Depr_promis", "Depr_qids", "Depr_Ans_dass", "Depr_Ans_hads", "Ans_gad", "Ans_tmas", "Ans_sas")
#######
```

### Scales related to anxiety and depression

Creating the dataframe and the group's list for all scales related to depression and anxiety
```{r, message=FALSE, warning=FALSE}
# Dataframe
df_anx_dp <- df[34:206]



# Groups
groups_anx_dep <- list(D_cesd = 1:20, D_phq = 21:29, D_promis = 30:57, D_qids = 58:73, A_dass = 74:80 , D_dass = 81:87 , A_hads = 88:94, D_hads = 95:101, A_gad = 102:108, A_sas = 109:123, A_tmas = 124:173)

```


### Scales related to anxiety and depression without TMAS

TMAS items are excluded because they are binary, unlike the Likert-scale items in the dataset, which could affect the accuracy of network analysis by increasing multicollinearity and distorting symptom relationships. Dichotomizing data, such as converting scores to binary categories, risks information loss, and while Cai (2022) uses binary data in network analysis, the potential impact of this on network structure is not addressed. Studies like Burger et al. (2022) advise caution when transforming data for network analysis, particularly with binarization. Excluding TMAS is a methodological choice that aims to ensure a more reliable and consistent analysis by using Likert scales for all symptoms.

```{r, message=FALSE, warning=FALSE}
# Dataframe

D_cesd <- df_anx_dp[1:20]
D_phq <- df_anx_dp[21:29]
D_promis <- df_anx_dp[30:57]
D_qids <- df_anx_dp[58:73]
A_dass <- df_anx_dp[c(74, 76, 78, 79, 82, 85, 86)] #74 ...80
D_dass <- df_anx_dp[c(75, 77, 80, 81, 83, 84, 87)] #81 ... 87 
A_hads <- df_anx_dp[c(88,90,92,94,96, 98, 100)] # 88 ... 94
D_hads <- df_anx_dp[c(89,91,93,95,97,99,101)] # 95 ... 101
A_gad <- df_anx_dp[102:108]
A_sas <- df_anx_dp[159:173] #109 ... 123
A_tmas <- df_anx_dp[109:158] #124 ... 174


df_anx_dp_adj <- as.data.frame(list(D_cesd, D_phq, D_promis, D_qids, A_dass, D_dass, A_hads, D_hads, A_gad, A_sas))



# Groups
groups_anx_dep_adj <- list(D_cesd = 1:20, D_phq = 21:29, D_promis = 30:57, D_qids = 58:73, A_dass = 74:80 , D_dass = 81:87 , A_hads = 88:94, D_hads = 95:101, A_gad = 102:108, A_sas = 109:123)

# To be more readable on Network Graphs here is a vector of shortenned names

readable_anx_dp <- c("c01", "c02", "c03", "c04", "c05", "c06", "c07", "c08", "c09", "c10", "c11", "c12", "c13", "c14", "c15", "c16", "c17", "c18", "c19", "c20", 
"ph01", "ph02", "ph03", "ph04", "ph05", "ph06", "ph07", "ph08", "ph09", 
"pr01", "pr02", "pr03", "pr04", "pr05", "pr06", "pr07", "pr08", "pr09", "pr10", "pr11", "pr12", "pr13", "pr14", "pr15", "pr16", "pr17", "pr18", "pr19", "pr20", "pr21", "pr22", "pr23", "pr24", "pr25", "pr26", "pr27", "pr28", 
"q01", "q02", "q03", "q04", "q05", "q06", "q07", "q08", "q09", "q10", "q11", "q12", "q13", "q14", "q15", "q16", 
"d02", "d04", "d07", "d09", "d15", "d19", "d20", "d03", "d05", "d10", "d13", "d16", "d17", "d21", 
"h01", "h03", "h05", "h07", "h09", "h11", "h13", "h02", "h04", "h06", "h08", "h10", "h12", "h14", 
"g01", "g02", "g03", "g04", "g05", "g06", "g07", 
"s01", "s02", "s03", "s04", "s05", "s06", "s07", "s08", "s09", "s10", "s11", "s12", "s13", "s14", "s15")  
#"t01", "t02", "t03", "t04", "t05", "t06", "t07", "t08", "t09", "t10", "t11", "t12", "t13", "t14", "t15", "t16", "t17", #"t18", "t19", "t20", "t21", "t22", "t23", "t24", "t25", "t26", "t27", "t28", "t29", "t30", "t31", "t32", "t33", "t34", #"t35", "t36", "t37", "t38", "t39", "t40", "t41", "t42", "t43", "t44", "t45", "t46", "t47", "t48", "t49", "t50")

# Group names
group_names_anx_dep <- c("Depr_cesd", "Depr_phq", "Depr_promis", "Depr_qids", "Ans_dass" , "Depr_dass" , "Ans_hads", "Depr_hads", "Ans_gad", "Ans_sas")
```


## Descriptive Statistics

### Demographics

```{r}
#to be done
```

### General Statistics about the scales

Summary, Graphs, range, mean, sd, etc...

```{r}
#to be done
```


## Force-directed plotting with Fruchterman–Reingold

Most studies on networks in psychopathology have used the Fruchterman-Reingold (FR) algorithm to create graphs (Borsboom et al., 2021). This algorithm is like setting up a system of balls connected by stretchy strings. The strings pull connected balls closer, while the other balls push them apart, resulting in a graph where nodes are well-spaced and edges are evenly distributed (Deserno et al., 2022).

The goal of force-directed algorithms is not to place nodes in specific meaningful locations, but to make the network easy to view, showing connections and clusters clearly. The arrangement produced by these algorithms is primarily driven by the need for visual clarity and does not necessarily reflect any inherent structure or meaning beyond the connections themselves. Therefore, it is crucial to focus on the connections between nodes and their strengths, rather than the spatial arrangement of nodes, when interpreting a force-directed graph (Deserno et al., 2022).

The spatial positions of nodes in these graphs are highly sensitive to variations in edge weights, even those as small as 0.01. A slight alteration in edge weights can lead to significant changes in the node arrangement (Burger et al., 2022). Therefore, the layout should not be interpreted as reflecting inherent properties or relationships among the nodes beyond their connection.


### Testing different correlation methods

Spearman Correlation, as mentioned, is particularly useful for analyzing non-parametric data. Spearman correlations, or rank-based correlations, can be used to handle non-normal continuous or ordered categorical data. On the other hand, automatic recognition of data type with cor_auto function from qgraph typically creates a dense correlation matrix, incorporating automatic correction for ordinal and continuous data, which can lead to multicollinearity. ForcePD forces the matrix to be positive definite. A positive definite matrix guarantees that all its eigenvalues are positive, a condition crucial for methods like testing the robustness of the network. Multicollinearity arises when predictor variables in a model are highly correlated, making it challenging to discern the unique effect of each predictor (Epskamp, Borsboom, & Fried, 2018). Therefore, testing which adjencency matrix is better in terms of multicollinearity and knowing whether it is positive.
The results below show that both matrices are positive definite but what actually indicates that Spearman is the most suitable method for our data is the amount of variable pairs over a threshold of 0.8. While Spearman hasarount 34 pairs with that extremelly high correlation, the cor_auto function has 1232 pairs.


```{r, warning=FALSE, message=FALSE}

# cor_auto
symp_auto <- cor_auto(df_anx_dp_adj, forcePD = TRUE)

# Spearman Correlation

symp_spear <- cor(df_anx_dp_adj, method = "spearman")


mc_auto <- multiC(symp_auto)
head(mc_auto, 5)
cat("\nAutomatic correlation method is positive definite = ", is.positive.definite(symp_auto), "\nIts amount of variable pairs over the threshold of 0.8 is:", nrow(mc_auto))

mc_spear <- multiC(symp_spear)
head(mc_spear, 5)
cat("\nSpearman method is positive definite = ", is.positive.definite(symp_spear), "\nIts amount of variable pairs over the threshold of 0.8 is:", nrow(mc_spear))
```


### Creating networks out of individual scales using FR algorithm and Spearman Correlation


The Spearman correlation is particularly useful for analyzing non-parametric data, such as those generated by Likert scales, which are commonly employed in psychological research. Likert scales typically consist of a set of statements or questions with ordered response categories, such as "strongly agree," and "strongly disagree". The ordered nature of these responses often violates the assumptions of parametric statistical methods that require continuous, normally distributed data (Blanken et al., 2022)*. Spearman correlation, as a non-parametric method, does not rely on these assumptions and can be used to assess the strength and direction of the association between variables measured on Likert scales. This makes it a valuable tool for examining relationships between variables that do not meet the criteria for parametric analyses, providing researchers with a robust alternative for analyzing data commonly encountered in psychological research.

```{r, warning=FALSE, message=FALSE}

n <- 1
for(sc in groups_anx_dep_adj){
  zero_order_scale <- cor(df_anx_dp_adj[sc], method = "spearman")
  qgraph(zero_order_scale, layout="spring", labels = colnames(zero_order_scale), color = sample(colors(), 1), theme="TeamFortress", height = 180, width = 140, title = paste("Network of", group_names_anx_dep[n]))

  n <- n + 1  
}

```






## Network graphs and analysis

At first glace, the items seem to be rather clustered together. In spite of the visual impression, it is crucial to explore some measures in order to explore the network.

```{r, fig.height=10, fig.width=14, warning=FALSE, message=FALSE, echo=FALSE}

color_nodes_anx_dep_adj <- c("darkblue", "darkgreen", "white", "black", "darkorange", "purple" , "grey", "yellow", "darkred", "darkgoldenrod4")


pdf("qgraph_spear.pdf")
anx_dep_spear <- qgraph(symp_spear, layout="spring", labels = readable_anx_dp, sampleSize = nrow(df_anx_dp_adj), groups = groups_anx_dep_adj, color = color_nodes_anx_dep_adj, theme="TeamFortress", label.prop=0.8, vsize=2, label.cex=1.1)
dev.off()

plot(anx_dep_spear)
```


### Networks by nosological entities
Identifying nodes only by the nosological entity one can see that the quantity of items related to depressive symptoms is far superior. It is no surprise since we excluded TMAS from the dataset.Anxiety items are in total 36 and the other 87 are related to depression. Despite representing a different nosological entity, these items seem to be clustered together with those of depression. Later, we investigate if the items about anxiety will form their own communities or blend with the others.

```{r, fig.height=8.5, fig.width=10, warning=FALSE, message=FALSE, echo=FALSE}
color_nodes_dual <- c("darkblue", "darkblue", "darkblue", "darkblue","darkred", "darkblue","darkred","darkblue","darkred","darkred")


qgraph(symp_spear, layout="spring", labels = readable_anx_dp,sampleSize = nrow(df_anx_dp_adj), groups = groups_anx_dep_adj, color = color_nodes_dual, theme="TeamFortress", label.prop=0.8, vsize=2, label.cex=1.1)

```

## Centrality Measures (Strength, Betweenness, Closeness):

Centrality measures are used to understand the relative importance or influence of nodes within a network. It is important to acknowledge that while centrality measures can provide valuable insights into the structure of a network, they should not be directly interpreted as measures of causal influence (Borsboom, 2017). The sources emphasize that network models, especially those based on correlation or partial correlation, do not inherently specify the direction of causal effects (Borsboom et al., 2021).

These measures help identify the most important nodes (symptoms) in the network. Strength indicates how connected a node is (Cai et al., 2022); Betweenness represents how often a node lies on the shortest path between other nodes; Closeness measures how quickly a node can reach other nodes.

```{r, warning=FALSE, message=FALSE, fig.height=14, fig.width=7.5}
# creating the table with all measures requested
cent_table_spear <- centrality_auto(symp_spear)

### Centrality Measures
pdf("centrality_spear.pdf")
cent_graph_spear <- centralityPlot(symp_spear, scale = "raw0", include = c("Strength", "Closeness", "Betweenness"), decreasing = T, labels = readable_anx_dp)
dev.off()
cent_graph_spear
```


####Strength

It is strength due to the fact that the connection between nodes used is a correlation zero-order matrix, thus a weight matrix. Therefore, Strength is the sum of the correlations of one node to all other nodes with higher values reflecting greater centrality in the network (Cai et al., 2022). There is a remarkable dominance of promis items among the strongest ones. All of them are arguably constructs of depressed mood.

```{r}
top_str <- cent_table_spear$node.centrality %>%
arrange(desc(Strength)) 

head(top_str, 10)
tail(top_str, 10)

cat("Top 5 Strength \n\n")
questions[c("promis_05", "promis_21", "promis_28","promis_15", "promis_02")] 

cat("\nBottom 5 Strength \n\n")
questions[c("cesd_11", "qids_07", "qids_08","qids_02", "qids_04")] 
```

####Betweenness

A node with high betweenness is a node that tends to connect clusters of nodes together (Deserno et al., 2022).

```{r}
top_bet <-cent_table_spear$node.centrality %>%
arrange(desc(Betweenness)) 

head(top_bet, 10)
tail(top_bet, 10)

cat("Top 5 Betweenness \n\n")
questions[c("phq_09", "cesd_05", "phq_05","cesd_18", "cesd_12")] 

cat("\nBottom Betweenness: 83 items had betweenness = 0 \n\n")
```

####Closeness

Closeness quantifies how far removed a node is from every other node in the network (Deserno et al., 2022).

```{r}
top_clo <- cent_table_spear$node.centrality %>%
arrange(Closeness) 

head(top_clo, 10) 
tail(top_clo, 10)

cat("Top 5 Closenness \n\n")
questions[c("qids_04", "qids_02", "qids_08","qids_09", "qids_07")] 

cat("\nBottom 5 Closenness \n\n")
questions[c("promis_05", "promis_28", "promis_21","promis_15", "promis_03")]
```

#### Intercorrelation of Centrality Measures:

This checks how centrality measures relate to each other. High intercorrelations suggest that certain centrality measures may be capturing similar network properties.

```{r}
cat("Correlation of the measures\n\n")
cat("Strength x Closeness: ", cor(cent_table_spear$node.centrality$Strength, cent_table_spear$node.centrality$Closeness, method="spearman"), "\n")
cat("Strength x Betweenness: ",cor(cent_table_spear$node.centrality$Strength, cent_table_spear$node.centrality$Betweenness, method="spearman"), "\n")
cat("Betweenness x Closeness: ",cor(cent_table_spear$node.centrality$Betweenness, cent_table_spear$node.centrality$Closeness, method="spearman"), "\n")


```

### Clustering 

The clustering coefficient measures how tightly connected the neighbors of a node are. High values indicate that a node's neighbors are also likely to be connected, forming local clusters of related symptoms.

#### Clustering Coefficient 

```{r, fig.height= 15, fig.width=8}

# Creating a copy of the symptom similarity matrix
cl_symp <- symp_spear

# Making the matrix symmetric by copying the upper triangle to the lower triangle
cl_symp[upper.tri(cl_symp)] <- t(cl_symp)[upper.tri(cl_symp)]

# Creating a clustering plot based on the symmetric similarity matrix
clusteringPlot(cl_symp, signed = T)


```


### Density and Small-Worldness (Transitivity, Average Path Length, Small-World Index):

Network density refers to the proportion of possible edges that are actually present. Small-worldness combines transitivity (the likelihood that two connected nodes share a neighbor) and average path length (the average number of steps between two nodes) to determine if the network has a small-world structure, where symptoms are highly clustered but still have short paths between them.

#### Density and smallworldness 

```{r, warning=FALSE, message=FALSE}

#Number of nodes: 
cat("Number of nodes: " ,ncol(symp_spear), "\n")
#Number of edges: 
cat("Number of Edges: ", sum(symp_spear[lower.tri(symp_spear)]), "\n")
#Density: 
cat("Density: ", mean(symp_spear[lower.tri(symp_spear)]), "\n")
 
#APL, transitivity and small-worldness: 
smallworldIndex(qgraph(symp_spear))
```


## 4. Robustness Network

```{r, warning=FALSE, message=FALSE}
### 4.1 edge weight bootstrap

#m1<-bootnet(df_anx_dp_adj, nBoots=500, default="EBICglasso", labels=colnames(df_anx_dp_adj), type="nonparametric", statistics =c("edge", "strength", "closeness", "betweenness"))
```


```{r, warning=FALSE, message=FALSE}
#save(m1, file = "boot_symp_df_edgeweights.Rdata")
load(file = "boot_symp_df_edgeweights.Rdata")

plot(m1, labels = FALSE, order = "sample")

pdf("boot_symp_df_edgeweights.pdf", useDingbats=FALSE) 
plot(m1, labels = FALSE, order = "sample")
dev.off()
```

```{r, warning=FALSE, message=FALSE}
#m2<- bootnet(df_anx_dp_adj, default = "EBICglasso", nBoots=500, type = "node", labels=colnames(df_anx_dp_adj), statistics =c("strength", "closeness", "betweenness"))
```

```{r, warning=FALSE, message=FALSE, fig.width=10, fig.height=14}
#save(m2, file = "boot_symp_df_nodedropping.Rdata")
load(file = "boot_symp_df_nodedropping.Rdata")

plot(m2)
plot(m2, perNode = T, legend = T, statistics =c("strength"))
#plot(m2, "betweenness", perNode = TRUE, legend = FALSE)
#plot(m2, "closeness", perNode = TRUE, legend = FALSE)
```


## Louvain Communities
** Explicar el concepto de louvain

### Creating the absolute values adjacency matrix

```{r}
# Converting the correlation matrix into an adjacency matrix
adj_matrix <- as.matrix(symp_spear)

# threshold to binarize the matrix (only keep strong correlations)
#adj_matrix[abs(adj_matrix) < 0.3] <- 0  # Set a threshold of 0.3 (or adjust as needed)

# attribute abs values to negative edges
adj_matrix[adj_matrix < 0] <- abs(adj_matrix[adj_matrix < 0])

# Converting the adjacency matrix to an igraph object
graph_symp <- graph_from_adjacency_matrix(adj_matrix, mode = "undirected", weighted = TRUE, diag = FALSE)

```

### Refining the resolution  
Changing resolution levels in order to find the most fine-grained set of communities. Counting the number of symptoms represented in all scales we arrived at 15 core symptoms related or not to DSM-V-TR. Using resolutions between 1.09 to 1.1 creates communities from 11 to 17 communities. Therefore, the idea of employing this range comes from the estimation of 15 main symptoms that we classified earlier. 
** ESCRIBIR SÍNTOMAS / PROFUNDIZAR

```{r}

# Running the Louvain algorithm 41 times to detect communities with a slowly growing modularity
decseq <- seq(from = 1.09, to = 1.1, by = 0.00025)
templist <- c()

# For loop to get all results as new columns
for(i in decseq){
  louvain_commu_temp <- cluster_louvain(graph_symp, resolution = i)
  comm_df <- as.data.frame(membership(louvain_commu_temp))
  
  templist[[as.character(i)]] <- comm_df}

louvain_rep <- as.data.frame(templist)
tlouvain <- t(louvain_rep)


#write.xlsx(as.data.frame(tlouvain), "louvain.xlsx", rowNames = TRUE)

```

### Choosing the best communities  
Find which result has the best correlation from all communities

```{r}
# Obtaining correlations
correlation_matrix <- cor(louvain_rep, method = "pearson")
clou <- as.data.frame(correlation_matrix)

#
colnames(clou)
# summing each column - summing is enough because all correlations are positive and have self cor values
l <- list()
for(i in colnames(clou)){
  cat(i, " = ",sum(clou[[i]]), "\n")
  l <- append(l, sum(clou[[i]]))
}

#value with the strongest correlations from all
clou[which.max(unlist(l))] 

```


## Creating the Network graph obtained with the best Louvain community

Each group has the name of the main symptom represented on its community. For example: the group related to suicide has some items related to weight loss and change of appetite. This happens likely because these items tend to cluster together 

```{r, fig.width=13, fig.height=10}
color_nodes_symp_df <- c("darkblue", "darkgreen", "limegreen", "darkorange", "purple", "grey", "yellow", "black", "black", "magenta", "brown", "darkorchid4" ,"white", "black" )

#modularidad .00065 R +- = 1.089 to 1.091

lsymp <- list('suicide' = c(1, 9, 11, 14, 15, 18, 28, 29, 49, 61, 63, 65, 69, 87), 'depressed_mood' = c(2, 4, 6, 22, 36, 44, 62), 'fatigue' = c(3,	7,	8,	10,	12,	13,	16,	20,	21,	24,	27), 'sleep' = c(5,	19,	23,	58,	59,	60), 'worthlessness' = c(17,	26,	30,	35,	37,	38,	39,	41,	56), 'increased_appetite' = c(25,	64,	66,	67,	68,	71,	72,	98,	115), 'hopeless_social' = c(31,	33,	34,	40,	42,	43,	46,	47,	48,	50,	51,	52,	53,	54,	55,	57), 'helpless' = c(32), "decision" = c(45) , 'anhedonia' = c(70,	95,	96,	97,	99,	100,	101), 'agitation' = c(73,	88,	90,	91,	93,	102,	103,	104,	105,	106,	107,	109,	111,	114), 'panic' = c(74,	75,	76,	77,	78,	79,	80,	89,	92,	94,	108,	110,	113,	116,	117,	118,	119,	120,	121,	122,	123), 'demotivation' = c(81,	82,	83,	84,	85,	86), 'no_control' = c(112))


qgraph(symp_spear, layout="spring", labels = colnames(df_anx_dp_adj),sampleSize = nrow(df_anx_dp_adj), groups = lsymp, color = color_nodes_symp_df, theme="TeamFortress", label.prop=0.8, vsize=2, label.cex=1)


```



