---
title: "exploratory_network_analysis"
author: "Pietro Olivetti, Max Comerma, Maria Barraza"
date: "2024-07-29"
output: html_document
---

Questions:
- How should I approach the sociodemographic data? 
- Should the values be transformed (Min-Max, Normalization)?
  - Which variables? Only the centrality measures?
- How to explore clusters?

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r functions, include=FALSE}
FR_net_by_scales_topnum_measures <- function(df, list_cols, top_number) # list_cols may have format: names = range (e.g.: cesd = 35:54)
{ 
  #unlisting cols to subset them
  vec_cols <- unlist(list_cols)

  ndf <- df[vec_cols]

  #creating correlation
  cor_mat <- cor(ndf)
  # creating indices to group by name

  
  
    update_indices <- function(indices, offset) {
    return(seq(from = 1 + offset, to = length(indices) + offset))
  }
  
  # Calculate the offset
  offset <- 0

  # Create the updated list of ranges
  updated_list_cols <- list()
  for (name in names(list_cols)) {
    updated_list_cols[[name]] <- update_indices(list_cols[[name]], offset)
    offset <- offset + length(list_cols[[name]])}
  
  
  # creating network  
qg <- qgraph(cor_mat, layout="spring", labels = colnames(cor_mat), groups = updated_list_cols ,color = sample(colors(), length(list_cols)), title = "Network of all items selected")

    
cent_net <- as.data.frame(centrality(qg)) 

# By degree
cent_net_degree <- cent_net%>%
  arrange(desc(OutDegree))
cent_net_degree <- cent_net_degree[1:top_number, ]

# By betweenness
cent_net_bet <- cent_net%>%
arrange(desc(Betweenness))
cent_net_bet <- cent_net_bet[1:top_number, ]

# By closeness
cent_net_clos <- cent_net%>%
arrange(desc(Closeness))
cent_net_clos <- cent_net_clos[1:top_number, ]



# Subsetting the top variables
cut_df_degree <- df[row.names(cent_net_degree)]
cor_cut_df_degree <- cor(cut_df_degree)

cut_df_bet <- df[row.names(cent_net_bet)]
cor_cut_df_bet <- cor(cut_df_bet)

cut_df_clos <- df[row.names(cent_net_clos)]
cor_cut_df_clos <- cor(cut_df_clos)

sel_measure_degree <- qgraph(cor_cut_df_degree, layout = "spring", labels = colnames(cor_cut_df_degree), theme="TeamFortress", title = paste("Network of the top", top_number, "nodes with the highest Degree"))

sel_measure_bet <- qgraph(cor_cut_df_bet, layout = "spring", labels = colnames(cor_cut_df_bet), theme="TeamFortress", title = paste("Network of the top", top_number, "nodes with the highest Betweenness"))

sel_measure_clos <- qgraph(cor_cut_df_clos, layout = "spring", labels = colnames(cor_cut_df_clos), theme="TeamFortress", title = paste("Network of the top", top_number, "nodes with the highest Closeness"))
  

  return(list(df = ndf, network =  qg, selected_bet = sel_measure_bet, selected_clos = sel_measure_clos, measures = cent_net, selected_degree = cent_net_degree, selected_betweenness = cent_net_bet, selected_closeness = cent_net_clos))
} 




FR_net_by_scales_top_measure <- function(df, list_cols, measure, top_number) # list_cols may have format: names = range (e.g.: cesd = 35:54)
{ measure <- tolower(measure)
  #unlisting cols to subset them
  vec_cols <- unlist(list_cols)
  #str_cols <- as.character(lapply(list_cols, function(x) x -  (min(unlist(list_cols)) - 1)))
  #subsetting
  ndf <- df[vec_cols]

  #creating correlation
  cor_mat <- cor(ndf)
  # creating indices to group by name

  
  
    update_indices <- function(indices, offset) {
    return(seq(from = 1 + offset, to = length(indices) + offset))
  }
  
  # Calculate the offset
  offset <- 0

  # Create the updated list of ranges
  updated_list_cols <- list()
  for (name in names(list_cols)) {
    updated_list_cols[[name]] <- update_indices(list_cols[[name]], offset)
    offset <- offset + length(list_cols[[name]])}
  
  
  # creating network  
qg <- qgraph(cor_mat, layout="spring", labels = colnames(cor_mat), groups = updated_list_cols ,color = sample(colors(), length(list_cols)))

    
cent_net <- as.data.frame(centrality(qg)) 
cent_net <- cent_net%>%
  arrange(case_when(
      measure == "outdegree" ~ desc(OutDegree),
      measure == "betweenness" ~ desc(Betweenness),
      measure == "closeness" ~ desc(Closeness)
    ))
cent_net <- cent_net[1:top_number, ]

# Subsetting the top variables
cut_df <- df[row.names(cent_net)]
cor_cut_df <- cor(cut_df)

sel_measure <- qgraph(cor_cut_df, layout = "spring", labels = colnames(cor_cut_df), theme="TeamFortress", title = paste("Network of the top", top_number, "nodes with the highest", measure))
  
  #qgraph(symp_zeroorder, layout="spring", labels = colnames(symp_zeroorder), color = sample(colors(), length(list_cols)), theme="TeamFortress", height = 180, width = 140, vsize=4)
  return(list(df = ndf, network =  qg, selected_network = sel_measure, selected_measures = cent_net))
}  

#test <- FR_net_by_scales_top_measure(df, list( Depr_cesd = 34:53, Depr_phq = 54:63, Depr_promis = 64:91, Depr_qids = 92:108), measure = 'closeness', top_number =  10)


aaa <- function(list_groups){update_indices <- function(indices, offset) {return(seq(from = 1 + offset, to = length(indices) + offset))}
  
  # Calculate the offset
  offset <- 0

  # Create the updated list of ranges
  updated_list_cols <- list()
  for (name in names(list_cols)) {
    updated_list_cols[[name]] <- update_indices(list_cols[[name]], offset)
    offset <- offset + length(list_cols[[name]])}}

```

# Network analysis of Depression and Anxiety Symptomatology

[Reference article](https://www.frontiersin.org/journals/psychology/articles/10.3389/fpsyg.2018.01742/full "Visualizing Psychological Networks: A Tutorial in R")

## Packages and loading

```{r packages, message=FALSE}
library(dplyr)
#library(igraph)
#library(igraphdata)
library(qgraph)
#library(bootnet)
#library(corpcor)
#library(usethis)
library(MPsychoR)
library(openxlsx)
library(ggplot2)
library(tidyr)
#library(png)
#library(gridExtra)
library(smacof)

```


```{r}
df <- read.csv('../data/data_cleaned.csv')[2:215]


```

## Grouping variables 

Ids = 1, Sociodem = 2:8, Pers_BFI2 = 9:23, Pers_hexaco = 24:33, Depr_cesd = 34:53, Depr_phq = 54:63, Depr_promis = 64:91, Depr_qids = 92:108, Depr_Ans_dass = 108:128, Depr_Ans_hads = 129:142, Ans_gad = 143:149, Ans_tmas = 150:199, Ans_sas = 200:214

```{r}
groups_all_variables <- list(Ids = 1, Sociodem = 2:8, Pers_BFI2 = 9:23, Pers_hexaco = 24:33, Depr_cesd = 34:53, Depr_phq = 54:63, Depr_promis = 64:91, Depr_qids = 92:108, Depr_Ans_dass = 108:128, Depr_Ans_hads = 129:142, Ans_gad = 143:149, Ans_tmas = 150:199, Ans_sas = 200:214)

groups_all_scales <- list(Pers_BFI2 = 9:23, Pers_hexaco = 24:33, Depr_cesd = 34:53, Depr_phq = 54:63, Depr_promis = 64:91, Depr_qids = 92:108, Depr_Ans_dass = 108:128, Depr_Ans_hads = 129:142, Ans_gad = 143:149, Ans_tmas = 150:199, Ans_sas = 200:214)

groups_anx_dep <- list(Depr_cesd = 34:53, Depr_phq = 54:63, Depr_promis = 64:91, Depr_qids = 92:108, Depr_Ans_dass = 108:128, Depr_Ans_hads = 129:142, Ans_gad = 143:149, Ans_tmas = 150:199, Ans_sas = 200:214)

groups_all_scales_adjusted <- list(Pers_BFI2 = 1:15, Pers_hexaco = 16:25, Depr_cesd = 26:45, Depr_phq = 46:55, Depr_promis = 56:83, Depr_qids = 84:100, Depr_Ans_dass = 101:121, Depr_Ans_hads = 122:135, Ans_gad = 136:142, Ans_tmas = 143:192, Ans_sas = 193:206)
  
groups_anx_dep_adjusted <- list(Depr_cesd = 1:20, Depr_phq = 21:30, Depr_promis = 31:58, Depr_qids = 59:75, Depr_Ans_dass = 76:95, Depr_Ans_hads = 96:109, Ans_gad = 110:116, Ans_tmas = 117:166, Ans_sas = 167:181)

```


## Force-directed plotting with Fruchterman–Reingold

Most studies on networks in psychopathology have used the Fruchterman-Reingold (FR) algorithm to create graphs. This algorithm is like setting up a system of balls connected by stretchy strings. The strings pull connected balls closer, while the other balls push them apart, resulting in a neat graph where nodes are well-spaced and edges are evenly distributed.

Force-directed algorithms aim to produce visually pleasing graphs by minimizing edge crossings and spacing nodes evenly. The goal is not to place the nodes in specific meaningful locations, but to make the network easy to view, showing connections and clusters clearly.

It's important to avoid interpreting the spatial positions of nodes in these graphs, as the placement is not meant to convey specific meanings. Misinterpreting the layout is a common mistake, as it's natural to want to find meaning in the arrangement.

The FR algorithm is the default in the qgraph R package, making it straightforward to use. 


### Creating individual scales networks using FR algorithm

These individual networks sho the connetions between the items. 

```{r}


group_names <- c("Ids", "Sociodem", "Pers_BFI2", "Pers_hexaco", "Depr_cesd", "Depr_phq", "Depr_promis", "Depr_qids", "Depr_Ans_dass", "Depr_Ans_hads", "Ans_gad", "Ans_tmas", "Ans_sas")

n <- 3
for(sc in groups_all_scales){
  zero_order <- cor(df[sc])
  qgraph(zero_order, layout="spring", labels = colnames(zero_order), color = sample(colors(), 1), theme="TeamFortress", height = 180, width = 140, title = paste("Network of", group_names[n]))
  n <- n + 1
}


```

### All the scales

```{r, fig.height=10, fig.width=10}




color_nodes <- c("darkgreen", "lightgreen", "deepskyblue", "dodgerblue", "royalblue", "navy", "darkorange", "orange", "lightcoral", "firebrick", "darkred")


gen_zeroorder <- cor(df[9:214])

qgraph(gen_zeroorder, layout="spring", labels = colnames(gen_zeroorder), groups = groups_all_scales_adjusted , color = color_nodes, theme="TeamFortress", height = 180, width = 140, vsize=3)


```

### Only the scales related to anxiety and depression

```{r, fig.height=10, fig.width=10}


color_nodes_anx_dep <- c("deepskyblue", "dodgerblue", "royalblue", "navy", "darkorange", "orange", "lightcoral", "firebrick", "darkred")


symp_zeroorder <- cor(df[34:214])
qgraph(symp_zeroorder, layout="spring", labels = colnames(symp_zeroorder), groups = groups_anx_dep_adjusted , color = color_nodes_anx_dep, theme="TeamFortress", label.prop=0.6, vsize=4)



```

### Networks of the top n measures of centrality

#### All Scales
Let's explore measures of centrality such as Strength (Degree), Betweenness and Closeness by sorting the all top results for each measure and creating a Network for each of them.


```{r}
all_cent_measures_25_top <- FR_net_by_scales_topnum_measures(df, list(Sociodem = 2:8, Pers_BFI2 = 9:23, Pers_hexaco = 24:33, Depr_cesd = 34:53, Depr_phq = 54:63, Depr_promis = 64:91, Depr_qids = 92:108, Depr_Ans_dass = 108:128, Depr_Ans_hads = 129:142, Ans_gad = 143:149, Ans_tmas = 150:199, Ans_sas = 200:214), 50)

cor_mat <- cor(df[2:214])
all_data_qg <- qgraph(cor_mat, layout="spring", labels = colnames(cor_mat), groups = groups_all_scales_adjusted ,color = color_nodes, title = "Network of all scales", theme="TeamFortress")


all_data_qg_cent <- centrality(all_data_qg)
all_data_qg_cent <- as.data.frame(all_data_qg_cent)

all_data_qg_cent_strength <- all_data_qg_cent %>%
arrange(desc(OutDegree)) %>%
select(Strength = OutDegree, Betweenness, Closeness, Influence = InExpectedInfluence)



round(all_cent_measures_25_top$selected_closeness[1:5],5)

all_data_qg
#row.names(all_cent_measures_25_top$selected_degree)
```

#####Strength 

It is strength due to the fact that the connection between nodes used is a correlation zero-order matrix, thus a weight matrix. Therefore, Strength is the sum of the correlations of one node to all other nodes with higher values reflecting greater centrality in the network (Cai et al., 2022). There is a remarkable dominance of promis items among the strongest ones. All of them are arguably constructs of depressed mood.

promis_28:	Me sentí completamente agotado/a emocionalmente -> Humor deprimido
promis_05:	Sentí que nada me podía animar -> Anhedonia / Humor deprimido
promis_15:	Me sentí deprimido/a -> Humor deprimido
promis_21:	Me sentí desesperanzado/a -> Humor deprimido
promis_07:	Me sentí triste -> Humor deprimido

```{r}
all_data_qg_cent_strength <- all_data_qg_cent %>%
arrange(desc(OutDegree)) %>%
select(Strength = OutDegree, Betweenness, Closeness, Influence = InExpectedInfluence)

all_data_qg_cent_strength
all_data_qgplot_cent_strength <- ggplot(all_data_qg_cent_strength, aes(Strength)) + geom_boxplot(color="darkblue",fill="lightblue",  outlier.colour = "red", show.legend = TRUE) + labs(title = "Strength of All items", x="Strength")

ggsave('../images/all_data_qgplot_cent_strength.png', all_data_qgplot_cent_strength)
```

#####Betweenness 

A node with high betweenness is a node that tends to connect clusters of nodes together (Deserno et al., 2022). The item 10 from BFI-2 is by far the one that seems to be more able to connect different clusters. As it is about having energy (or lacking it), it seems plausible to hypothetize that the energy level is a component that interconnects clusters of symptoms.

bfi2_10:		Lleno/a de energía
tmas_26.	Tengo plena confianza en mí mismo/a
bfi2_12:		Que tiende a sentirse deprimido/a, melancólico/a
hads_13:	Me asaltan sentimientos repentinos de pánico
qids_12:	Pensamientos sobre la muerte o el suicidio

```{r}
all_data_qg_cent_betweenness <- all_data_qg_cent %>%
arrange(desc(Betweenness)) %>%
select(Betweenness, Strength = OutDegree, Closeness, Influence = InExpectedInfluence)

all_data_qg_cent_betweenness
all_data_qgplot_cent_betweenness <- ggplot(all_data_qg_cent_betweenness, aes(Betweenness)) + geom_boxplot(color="darkblue",fill="lightblue",  outlier.colour = "red", show.legend = TRUE) + labs(title = "Betweenness of All items", x="Betweenness")

ggsave('../images/all_data_qgplot_cent_betweenness.png', all_data_qgplot_cent_betweenness)
```

#####Closeness 

Closeness quantifies how far removed a node is from every other node in the network (Deserno et al., 2022). As in Strength, there is a dominance of promis items among the ones that are more influential on closeness. Also, all of them seem to be constructs of depressed mood.

promis_28:	Me sentí completamente agotado/a emocionalmente -> Humor deprimido
promis_05:	Sentí que nada me podía animar -> Anhedonia / Humor deprimido
promis_07:	Me sentí triste -> Humor deprimido
promis_21:	Me sentí desesperanzado/a -> Humor deprimido
promis_15:	Me sentí deprimido/a -> Humor deprimido



```{r}
all_data_qg_cent_closeness <- all_data_qg_cent %>%
arrange(desc(Closeness)) %>%
select(Closeness, Strength = OutDegree, Betweenness, Influence = InExpectedInfluence)

all_data_qg_cent_closeness
all_data_qgplot_cent_closeness <- ggplot(all_data_qg_cent_closeness, aes(Closeness)) + geom_boxplot(color="darkblue",fill="lightblue",  outlier.colour = "red", show.legend = TRUE) + labs(title = "Closeness of All items", x="Closeness")

ggsave('../images/all_data_qgplot_cent_closeness.png', all_data_qgplot_cent_closeness)
```


#### Depression and Anxiety Scales

```{r}
anx_dep_cent_measures_25_top <- FR_net_by_scales_topnum_measures(df, list(Depr_cesd = 34:53, Depr_phq = 54:63, Depr_promis = 64:91, Depr_qids = 92:108, Depr_Ans_dass = 108:128, Depr_Ans_hads = 129:142, Ans_gad = 143:149, Ans_tmas = 150:199, Ans_sas = 200:214), 10)

anx_dep_cent_measures_25_top$selected_degree[1:5]
anx_dep_cent_measures_25_top$selected_betweenness[1:5]
anx_dep_cent_measures_25_top$selected_closeness[1:5]
```
```{r, fig.height=20}
centralityPlot(symp_zeroorder, scale = "raw0", include = c("Strength", 
"Closeness", "Betweenness", "ExpectedInfluence"))
```

#### Escalas de Ansiedad y depresión

### Removing most influential nodes

#### Closeness

#### Betweenness

#### Degree

#### Progressive construccion of the network
By joining step by step

## Multidimensional Scaling (MDS) of Networks 

MDS represents proximities among variables as distances between points in a low-dimensional space (e.g., two or three dimensions; Mair et al., 2016). Proximity is an umbrella term for “similarities” between variables (e.g., correlation) or “dissimilarities” (e.g., Euclidean distance). Because MDS helps represent complex data in low-dimensional space, it dovetails precisely with the goal of visual presentation of complex psychological networks. That is, we can use MDS to represent proximities in a two-dimensional space (e.g., X & Y) to produce two-dimensional network plots. MDS is particularly useful for understanding networks because the distances between plotted nodes are interpretable as Euclidean distances.

Because the smacof R package (De Leeuw and Mair, 2009) requires dissimilarities (rather than similarities) as input, we will convert the correlation matrix into a dissimilarity matrix.

```{r}
groups <- list(Pers_BFI2 = 9:23, Pers_hexaco = 24:33, Depr_cesd = 34:53, Depr_phq = 54:63, Depr_promis = 64:91, Depr_qids = 92:108, Depr_Ans_dass = 108:128, Depr_Ans_hads = 129:142, Ans_gad = 143:149, Ans_tmas = 150:199, Ans_sas = 200:214)

n <- 3
for(sc in groups){
  zero_order_md <- cor(df[sc])
  qgraph(zero_order_md, layout="spring", labels = colnames(zero_order_md), color = sample(colors(), 1), theme="TeamFortress", height = 180, width = 140, title = paste("MDS Network of", group_names[n]))
  n <- n + 1
}

```

### Transformations

Shepard diagrams allow us to visualize how well our MDS configuration fits our dissimilarity matrix. When the dissimilarities align in a linear fashion, a ratio or interval MDS is most appropriate. In other cases, a nonlinear transformation such as ordinal MDS or spline MDS may be more appropriate. The normalized stress values (plotted in each graph) can help guide us in deciding which transformation provides the best fit.

#### Shepard diagrams for all scales

It's possible to see that Spline and Ordinal MDS are the transformations with less stress, with the later showing a slightly better result.

```{r}

gen_zeroorder <- cor(df[9:214])

dissimilarities <- sim2diss(gen_zeroorder)

MDS_ordinal <- mds(dissimilarities, type = 'ordinal')
plot(MDS_ordinal, plot.type = "Shepard", main = "Ordinal")
text(1.1,0.3, paste("Stress =", round(MDS_ordinal$stress,2)))

MDS_ratio <- mds(dissimilarities, type = "ratio")
plot(MDS_ratio, plot.type = "Shepard", main = "Ratio")
text(1.1,0.3, paste("Stress =", round(MDS_ratio$stress,2)))

MDS_interval <- mds(dissimilarities, type = "interval")
plot(MDS_interval, plot.type = "Shepard", main = "Interval")
text(1.1,0.3, paste("Stress =", round(MDS_interval$stress,2)))

MDS_mspline <- mds(dissimilarities, type = "mspline")
plot(MDS_mspline, plot.type = "Shepard", main = "Spline")
text(1.1,0.3, paste("Stress =", round(MDS_mspline$stress,2)))
```

#### All the scales with MDS Ordinal transformation
```{r}


groups <- list(Pers_BFI2 = 1:15, Pers_hexaco = 16:25, Depr_cesd = 26:45, Depr_phq = 46:55, Depr_promis = 56:83, Depr_qids = 84:100, Depr_Ans_dass = 101:120, Depr_Ans_hads = 121:134, Ans_gad = 135:141, Ans_tmas = 142:191, Ans_sas = 192:206)


color_nodes <- c("darkgreen", "lightgreen", "deepskyblue", "dodgerblue", "royalblue", "navy", "darkorange", "orange", "lightcoral", "firebrick", "darkred")


gen_zeroorder <- cor(df[9:214])

qgraph(gen_zeroorder, layout=MDS_ordinal$conf, labels = colnames(gen_zeroorder), groups = groups , color = color_nodes, theme="TeamFortress", height = 180, width = 140, vsize=3)
```


#### Depression and anxiety scales with MDS Ordinal transformation

```{r}
dep_anx_mds_qg <- qgraph(symp_zeroorder, layout= MDS_ordinal$conf, labels = colnames(symp_zeroorder), groups = groups_anx_dep , color = color_nodes_anx_dep, theme="TeamFortress", vsize=2)

```

# From this point consider all a draft

### Centrality Measures on MDS (to continue...)

Let's explore the centrality. We order the items with the highest outdegrees and, then, highest Betweenness. Outdegree in a correlation matrix network could be defined as the sum of variable correlations that have edges with a specific node. Due to the nature of the undirected edges based on correlation matrices, outdegrees and indegrees are redundant measures. In the code below we will identify the 50 most influential nodes and build a matrix network with them.

```{r}

centrality_dep_anx_mds_qg <- centrality(dep_anx_mds_qg) 
  
centrality_dep_anx_mds_qg <- as.data.frame(centrality_dep_anx_mds_qg) %>%
arrange(desc(OutDegree), desc(Betweenness))

cent_dep_anx_mds_qg_50_degrees <- as.vector(rownames(centrality_dep_anx_mds_qg))[1:50]

sub_top50_degree_df <- df[cent_dep_anx_mds_qg_50_degrees]

sub_top50_degree_df_cor <- cor(sub_top50_degree_df)

diss_sub_top50_degree_df <- sim2diss(sub_top50_degree_df_cor)

MDS_ord_sub_top50_degree <- mds(dissimilarities, type = 'ordinal')


qgraph(sub_top50_degree_df_cor, layout= MDS_ord_sub_top50_degree$conf, labels = colnames(sub_top50_degree_df_cor),  vsize=4)


```




```{r}
z_central <- (centrality_dep_anx_mds_qg$OutDegree - mean(centrality_dep_anx_mds_qg$OutDegree)) / sd(centrality_dep_anx_mds_qg$OutDegree)
z_bet <- (centrality_dep_anx_mds_qg$Betweenness - mean(centrality_dep_anx_mds_qg$Betweenness)) / sd(centrality_dep_anx_mds_qg$Betweenness)
```

```{r}

mm_central <- ((centrality_dep_anx_mds_qg$OutDegree - min(centrality_dep_anx_mds_qg$OutDegree)) / (max(centrality_dep_anx_mds_qg$OutDegree) - min(centrality_dep_anx_mds_qg$OutDegree))) * 3

mm_bet <- ((centrality_dep_anx_mds_qg$Betweenness - min(centrality_dep_anx_mds_qg$Betweenness)) / (max(centrality_dep_anx_mds_qg$Betweenness) - min(centrality_dep_anx_mds_qg$Betweenness))) * 3
```

```{r}
plot_output <- centralityPlot(dep_anx_mds_qg)

plot_output + theme(plot.margin = margin(t = 0.1, r = 0.10, b = 0.10, l = 0.10, unit = "cm"), label.cex = 1)

ggsave("my_plot.png", plot_output, width = 10, height = 20, units = "in", limitsize = FALSE)

clusteringPlot(dep_anx_mds_qg)
```

```{r}
centrality_dep_anx_mds_qg <- centrality(dep_anx_mds_qg)

centrality_dep_anx_mds_qg <- as.data.frame(centrality_dep_anx_mds_qg) %>%
arrange(desc(OutDegree), desc(Betweenness))

centrality_dep_anx_mds_qg[1:5]
```
```{r, fig.width=15, fig.height=10}

qgraph(symp_zeroorder, layout= MDS_ordinal$conf, labels = colnames(symp_zeroorder), groups = groups_anx_dep , color = color_nodes_anx_dep, theme="TeamFortress", vsize=mm_central)

```

```{r}

```


```{r}

```

```{r}
bet_all_25top

mmdf <- as.data.frame(mm_bet) 
mmdf%>%
  arrange(desc(mmdf))
```
- bfi2_10		Lleno/a de energía
- tmas_26	Tengo plena confianza en mí mismo/a
- bfi2_12		Que tiende a sentirse deprimido/a, melancólico/a

```{r, fig.height=10, fig.width=10}


bet_all_25top <- all_cent_measures_25_top$selected_betweenness[1:5]


gr <- row.names(bet_all_25top)

all_zeroorder <- cor(df[2:214])

qg_bet <- qgraph(all_zeroorder, layout="spring", labels = colnames(all_zeroorder), groups = list(bfi2_10 = 17, tmas_26 = 174, bfi2_12 = 19) , color = "darkgreen", theme="TeamFortress", vsize=3)

qb_bet <- centrality(qg_bet)

mm_bet <- ((qb_bet$Betweenness - min(qb_bet$Betweenness)) / (max(qb_bet$Betweenness) - min(qb_bet$Betweenness))) * 5


qgraph(all_zeroorder, layout="spring", groups = index_list , color = c(sample(colors(), length(index_list))), vsize=mm_bet, labels = FALSE)
```

```{r}
by_cent_measure_top10 <- FR_net_by_scales_topnum_measures(df, groups, 10) # groups is a list that has personality scales

by_cent_measure_top10$selected_

groups

nodes_by_metrics_all <- function(df, qg){
  all_zeroorder <- cor(df)
  
}
```


```{r}
```


```{r}

index_vector <- c()
for(col in gr)
{
index_vector <- c(index_vector ,which(names(df) == col))
}

index_vector


index_list <- setNames(as.list(index_vector - 1), gr)
index_list
```