---
title: "net_exp_draft"
author: "Pietro Olivetti"
date: "2024-10-01"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
  chunk_output_type: inline
---

# Network analysis of Depression and Anxiety Symptomatology

## Questions:

-   Should we use Multidimensional Scaling? (proximities among variables
    as distances between points in a low-dimensional space (e.g., two or
    three dimensions; Mair et al., 2016). Proximity is an umbrella term
    for “similarities” between variables (e.g., correlation) or
    “dissimilarities” (e.g., Euclidean distance). Because MDS helps
    represent complex data in low-dimensional space, it dovetails
    precisely with the goal of visual presentation of complex
    psychological networks. That is, we can use MDS to represent
    proximities in a two-dimensional space (e.g., X & Y) to produce
    two-dimensional network plots. MDS is particularly useful for
    understanding networks because the distances between plotted nodes
    are interpretable as Euclidean distances.

-   How should the binary TMAS items be treated?

-   Finding Louvain communities makes sense for this project?

-   

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages and loading

```{r packages, message=FALSE}
library(dplyr)
library(igraph)
#library(igraphdata)
library(qgraph)
library(bootnet)
#library(corpcor)
#library(usethis)
#library(MPsychoR)
library(openxlsx)
library(ggplot2)
library(tidyr)
#library(png)
#library(gridExtra)
#library(smacof)

```

```{r}
df <- read.csv('../data/data_cleaned_temp.csv')

```

## General Infomation

### Separating groups

Ids = 1, Sociodem = 2:8, Pers_BFI2 = 9:23, Pers_hexaco = 24:33,
Depr_cesd = 34:53, Depr_phq = 54:62, Depr_promis = 63:90, Depr_qids =
91:106, Depr_Ans_dass = 107:120, Depr_Ans_hads = 121:134, Ans_gad =
135:141, Ans_tmas = 142:191, Ans_sas = 192:206

```{r}
groups_all_variables <- list(Ids = 1, Sociodem = 2:8, Pers_BFI2 = 9:23, Pers_hexaco = 24:33, Depr_cesd = 34:53, Depr_phq = 54:62, Depr_promis = 63:90, Depr_qids = 91:106, Depr_Ans_dass = 107:120, Depr_Ans_hads = 121:134, Ans_gad = 135:141, Ans_tmas = 142:191, Ans_sas = 192:206)

########
groups_all_scales <- list(Pers_BFI2 = 1:15, Pers_hexaco = 16:25, Depr_cesd = 26:45, Depr_phq = 46:54, Depr_promis = 55:82, Depr_qids = 83:98, Depr_Ans_dass = 99:112, Depr_Ans_hads = 113:126, Ans_gad = 127:133, Ans_tmas = 134:183, Ans_sas = 184:198)

df_all_scales <- df[9:206]
#######


groups_anx_dep <- list(Depr_cesd = 1:20, Depr_phq = 21:29, Depr_promis = 30:57, Depr_qids = 58:73, Depr_Ans_dass = 74:87, Depr_Ans_hads = 88:101, Ans_gad = 102:108, Ans_tmas = 109:158, Ans_sas = 159:173)

df_anx_dp <- df[34:206]

#######

group_names <- c("Ids", "Sociodem", "Pers_BFI2", "Pers_hexaco", "Depr_cesd", "Depr_phq", "Depr_promis", "Depr_qids", "Depr_Ans_dass", "Depr_Ans_hads", "Ans_gad", "Ans_tmas", "Ans_sas")



```

### Demographics

```{r}

```

### General Statistics about the scales

Summary, Graphs, range, mean, sd, etc...

```{r}

```

## Force-directed plotting with Fruchterman–Reingold

Most studies on networks in psychopathology have used the
Fruchterman-Reingold (FR) algorithm to create graphs. This algorithm is
like setting up a system of balls connected by stretchy strings. The
strings pull connected balls closer, while the other balls push them
apart, resulting in a graph where nodes are well-spaced and edges are
evenly distributed.

Force-directed algorithms aim to produce visually pleasing graphs by
minimizing edge crossings and spacing nodes evenly. The goal is not to
place the nodes in specific meaningful locations, but to make the
network easy to view, showing connections and clusters clearly.

It's important to avoid interpreting the spatial positions of nodes in
these graphs, as the placement is not meant to convey specific meanings.
Misinterpreting the layout is a common mistake, as it's natural to want
to find meaning in the arrangement.

### Creating individual scales networks using FR algorithm

These individual networks shows the connections between the items.

```{r}

#zero_order <- cor_auto(df_all_scales)

# Start Naming from the 
n <- 3
for(sc in groups_all_scales){
  zero_order_scale <- cor_auto(df_all_scales[sc])
  qgraph(zero_order_scale, layout="spring", labels = colnames(zero_order_scale), color = sample(colors(), 1), theme="TeamFortress", height = 180, width = 140, title = paste("Network of", group_names[n]))
  n <- n + 1  
}
```

### All the scales

```{r, fig.height=10, fig.width=10}

zero_order <- cor_auto(df_all_scales)


color_nodes <- c("darkgreen", "lightgreen", "deepskyblue", "dodgerblue", "royalblue", "navy", "darkorange", "orange", "lightcoral", "firebrick", "darkred")


qg_all_scales <-qgraph(zero_order, layout="spring", labels = colnames(zero_order), groups = groups_all_scales , color = color_nodes, theme="TeamFortress", height = 180, width = 140, vsize=1.5)


```

### Only the scales related to anxiety and depression

For now on the scales related to the symptoms will be on focus. If it
seems convenient in a future point of the research we will use
Personality scales again.

```{r, fig.height=10, fig.width=10}


color_nodes_anx_dep <- c("deepskyblue", "dodgerblue", "royalblue", "navy", "darkorange", "orange", "lightcoral", "firebrick", "darkred")


symp_zeroorder <- cor_auto(df_anx_dp)

anx_dep_FR <- qgraph(symp_zeroorder, layout="spring", labels = colnames(symp_zeroorder), groups = groups_anx_dep, color = color_nodes_anx_dep, theme="TeamFortress", label.prop=0.6, vsize=1.5)


```

### Network by gender and other sociodemographic data

```{r}

```

### Glasso and Robustness

When estimating networks using glasso (graphical lasso), we apply it to
a covariance matrix to create a sparse network by setting many edges
(relationships) to zero, reducing false positives. The code below
performs 1,000 bootstrap samples to evaluate the network's stability. It
uses the EBICglasso method, which combines the Extended Bayesian
Information Criterion (EBIC) with graphical lasso to estimate a sparse
network and control for false positives. The "nonparametric" option
ensures that bootstrapping resamples the data without assuming a
specific statistical distribution. Lasso applies a penalty, shrinking
weaker relationships to zero to simplify the model.

```{r, fig.height=10, fig.width=10}
# checking min value
min(symp_zeroorder)

# checking max value
max(symp_zeroorder)

symp_centrality <- centrality_auto(anx_dep_FR)


##### 3. Network 1: 
graph_all_scales_FR <-EBICglasso(zero_order, n = nrow(df_all_scales), gamma = 0)

cor(symp_zeroorder)
symp_zeroorder

symp_zeroorder_reg <- symp_zeroorder + diag(1e-4, ncol(symp_zeroorder))
det(symp_zeroorder_reg)  # Check if it's now positive definite

eigenvalues <- eigen(symp_zeroorder)$values
eigenvalues

symp_zeroorder_reg <- symp_zeroorder + diag(1e-2, ncol(symp_zeroorder))  # Increase to 0.01 or higher

eigenvalues <- eigen(symp_zeroorder_reg)$values
eigenvalues

library(corrplot)
corrplot(cor(df_anx_dp), method = "color", tl.col = "black", tl.srt = 45)

estimateNetwork(df_anx_dp, default = "EBICglasso", corMethod = "cor_auto", missing = "pairwise")

dfcesd <- df[34:90]

#estimateNetwork(dfcesd, default = "EBICglasso", corMethod = "cor_auto", missing = "pairwise")
c.dfcesd <- cor_auto(dfcesd)
EBICglasso(c.dfcesd, n = nrow(dfcesd))

library(corpcor)

t.dfcesd <- cov.shrink(diff(as.matrix(c.dfcesd)))

EBICglasso(t.dfcesd, n = nrow(dfcesd))


t.symp_zeroorder <- cov.shrink(diff(as.matrix(symp_zeroorder)))

ebicglasso.symp <- EBICglasso(t.symp_zeroorder, n = nrow(df_anx_dp))

eg <-qgraph(ebicglasso.symp, layout="spring", labels = colnames(ebicglasso.symp), groups = groups_anx_dep, color = color_nodes_anx_dep, theme="TeamFortress", label.prop=0.6, vsize=2.5)

arrange(as.data.frame(centrality_auto(eg)))
```

```{r, fig.height=10, fig.width=10}
## Robustness

m1<-bootnet(df_anx_dp, nBoots=1000, default="EBICglasso", labels=df_anx_dp, type="nonparametric")
save(m1, file = "boot_df_anx_dp_edgeweights.Rdata")
load(file = "boot_df_anx_dp_edgeweights.Rdata")
m1
```

### Measures of centrality

```{r}

all_data_qg_cent <- centrality(all_data_qg)
all_data_qg_cent <- as.data.frame(all_data_qg_cent)


symp_qg_betweenness <- all_data_qg_cent %>%
arrange(desc(Betweenness)) %>%
select(Betweenness, Strength = OutDegree, Closeness, Influence = InExpectedInfluence)
```

####Strength

It is strength due to the fact that the connection between nodes used is
a correlation zero-order matrix, thus a weight matrix. Therefore,
Strength is the sum of the correlations of one node to all other nodes
with higher values reflecting greater centrality in the network (Cai et
al., 2022). There is a remarkable dominance of promis items among the
strongest ones. All of them are arguably constructs of depressed mood.

promis_21: Me sentí desesperanzado/a -\> Humor deprimido promis_05:
Sentí que nada me podía animar -\> Anhedonia / Humor deprimido sas_04:
Siento que me estoy desmoronando promis_28: Me sentí completamente
agotado/a emocionalmente -\> Humor deprimido promis_03: Me sentí
indefenso/a (que no podía hacer nada para ayudarme)

```{r}
symp_centrality$node.centrality %>%
arrange(desc(Strength)) %>%
select(Strength, Betweenness, Closeness, ExpectedInfluence)
```

####Betweenness

A node with high betweenness is a node that tends to connect clusters of
nodes together (Deserno et al., 2022).

```{r}
symp_centrality$node.centrality %>%
arrange(desc(Betweenness)) %>%
select( Betweenness, Strength, Closeness, ExpectedInfluence)
```

####Closeness

Closeness quantifies how far removed a node is from every other node in
the network (Deserno et al., 2022).

```{r}
symp_centrality$node.centrality %>%
arrange(Closeness) %>%
select(Closeness, Strength, Betweenness, ExpectedInfluence)
```

#### Plot

```{r}

n <- 5
for(sc in groups_anx_dep){
  zero_order_scale <- cor_auto(df_anx_dp[sc])
  centralityPlot(zero_order_scale, scale = "raw0", include = c("Strength", "Closeness", "Betweenness", "ExpectedInfluence"))
  #, title = paste("Network of", group_names[n]))

  n <- n + 1  
}
```

```{r, fig.height=20, fig.width=10}
centralityPlot(symp_zeroorder, scale = "raw0", include = c("Strength", 
"Closeness", "Betweenness", "ExpectedInfluence"), decreasing = T)
```

### Intercorrelation of different centrality measures

```{r}

cor(----$InDegree, ----$Closeness, method="spearman")    
cor(----$InDegree, ----$Betweenness, method="spearman")   
cor(----$Betweenness, ----$Closeness, method="spearman")
```

### Density, bridge centrality and smallworldness

```{r}

```

## Lasso and EBIC

A main advantage of the network approach is that it visualizes the
multivariate dependencies of the data that otherwise remain hidden. The
most informative visualization, which we also choose here, is one in
which edges can be understood as partial correlation coefficients,
meaning that a connection between nodes A and B is the connection after
controlling for all other edges in the network. To do so, we estimated a
Gaussian Graphical Model that estimates pairwise association parameters
between all nodes.The estimation of that many parameters likely leads to
a number of false positive connections, and we control for these by
using the least absolute shrinkage and selection operator (LASSO)
(Tibshirani, 1996) that sets very small edges to zero. In other words,
the LASSO procedure employs a regularization technique that
conservatively identifies only the relevant edges, and accurately
discovers the underlying network structure (van Borkulo et al., 2014)
Armour, Fried et al. 2016

```{r}
library(glasso)

adj_matrix <- as.matrix(df_anx_dp)

# mt <- cor_auto(df_anx_dp) doesn't work
mt <- cor(df_anx_dp)
qsymp <-EBICglasso(adj_matrix, n = nrow(df_anx_dp)) 
# qsymp <-EBICglasso(mt, n = nrow(df_anx_dp)) 


qsymp

# Count non-diagonal elements
length(----[upper.tri(qsymp)]) #qsymp or mt?
```

## Robustness

```{r}
##### 4. Robustness Network 1: Anxiety and Depressive symptoms

### 4.1 edge weight bootstrap

m1<-bootnet(df_anx_dp, nBoots=1000, default="EBICglasso", labels=df_anx_dp, type="nonparametric")
save(m1, file = "boot_df_anx_dp_edgeweights.Rdata")
load(file = "boot_df_anx_dp_edgeweights.Rdata")

plot(m1, labels = FALSE, order = "sample")

pdf("boot_df_anx_dp_edges.pdf", useDingbats=FALSE) 
plot(m1, labels = FALSE, order = "sample")
dev.off()

m1
```

## Clustering

### Clustering Coefficient

```{r}

clustcoef_auto(symp_zeroorder)

clusteringPlot(symp_zeroorder)
```

### Finding Communities

```{r}
# 1. Convert the correlation matrix into an adjacency matrix
adj_matrix <- as.matrix(symp_zeroorder)

# Optional: Apply a threshold to binarize the matrix (only keep strong correlations)
#adj_matrix[abs(adj_matrix) < 0.3] <- 0  # Set a threshold of 0.3 (or adjust as needed)

# attribute abs values to negative edges
adj_matrix[adj_matrix < 0] <- abs(adj_matrix[adj_matrix < 0])

# 2. Convert the adjacency matrix to an igraph object
graph_symp <- graph.adjacency(adj_matrix, mode = "undirected", weighted = TRUE, diag = FALSE)


# 3. Run the Louvain algorithm to detect communities
louvain_communities <- cluster_louvain(graph_symp)

# 4. Print the community memberships
membership(louvain_communities)


#plot(graph_symp, vertex.color=membership(louvain_communities))
#plot(graph_symp, vertex.color=membership(louvain_communities), layout=layout_nicely(graph_symp), vertex.size=5, vertex.shape="sphere", edge.width=2, edge.arrow=TRUE)

louvain_communities$modularity

groups(louvain_communities)
a
```

# 

```{r}
a <- cent_table_spear$node.centrality

which(colnames(df_anx_dp_adj) == 'hads_11')

df_anx_dp_adj[88:95]

b <- cent_table_spear$edge.betweenness.centrality
```




```{r}
pers <- cor(df_all_scales, method = "spearman")

aaa <- multiC(pers)

net_pers <- qgraph(pers, layout="spring", labels = colnames(df_all_scales),sampleSize = nrow(df_all_scales), groups = groups_all_scales, color = color_nodes_symp_df, theme="TeamFortress", label.prop=0.8, vsize=2, label.cex=1)

is.positive.definite(pers)

net_pers_cent <- centrality_auto(net_pers)


nc <- net_pers_cent$node.centrality


nc %>% arrange(desc(Betweenness))

nc %>% arrange(desc(Strength))

nc %>% arrange(desc(Closeness))
```


```{r}
pers <- cor(df_anx_dp, method = "spearman")

aaa <- multiC(pers)

net_pers <- qgraph(pers, layout="spring", labels = colnames(df_anx_dp),sampleSize = nrow(df_anx_dp), groups = groups_anx_dep, color = color_nodes_symp_df, theme="TeamFortress", label.prop=0.8, vsize=2, label.cex=1)

is.positive.definite(pers)

net_pers_cent <- centrality_auto(net_pers)


nc <- net_pers_cent$node.centrality


nc %>% arrange(desc(Betweenness))

nc %>% arrange(desc(Strength))

nc %>% arrange(desc(Closeness))
```

```{r}

est <- estimateNetwork(df_anx_dp, default = "EBICglasso")

is.positive.definite(est$graph)
```


