---
title: "exploratory_network_analysis_draft"
author: "Pietro Olivetti"
date: "2024-09-28"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

Questions: - How should I approach the sociodemographic data? - Should
the values be transformed (Min-Max, Normalization)? - Which variables?
Only the centrality measures? - How to explore clusters?

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r functions, include=FALSE}
FR_net_by_scales_topnum_measures <- function(df, list_cols, top_number) # list_cols may have format: names = range (e.g.: cesd = 35:54)
{ 
  #unlisting cols to subset them
  vec_cols <- unlist(list_cols)

  ndf <- df[vec_cols]

  #creating correlation
  cor_mat <- cor(ndf)
  # creating indices to group by name

  
  
    update_indices <- function(indices, offset) {
    return(seq(from = 1 + offset, to = length(indices) + offset))
  }
  
  # Calculate the offset
  offset <- 0

  # Create the updated list of ranges
  updated_list_cols <- list()
  for (name in names(list_cols)) {
    updated_list_cols[[name]] <- update_indices(list_cols[[name]], offset)
    offset <- offset + length(list_cols[[name]])}
  
  
  # creating network  
qg <- qgraph(cor_mat, layout="spring", labels = colnames(cor_mat), groups = updated_list_cols ,color = sample(colors(), length(list_cols)), title = "Network of all items selected")

    
cent_net <- as.data.frame(centrality(qg)) 

# By degree
cent_net_degree <- cent_net%>%
  arrange(desc(OutDegree))
cent_net_degree <- cent_net_degree[1:top_number, ]

# By betweenness
cent_net_bet <- cent_net%>%
arrange(desc(Betweenness))
cent_net_bet <- cent_net_bet[1:top_number, ]

# By closeness
cent_net_clos <- cent_net%>%
arrange(desc(Closeness))
cent_net_clos <- cent_net_clos[1:top_number, ]



# Subsetting the top variables
cut_df_degree <- df[row.names(cent_net_degree)]
cor_cut_df_degree <- cor(cut_df_degree)

cut_df_bet <- df[row.names(cent_net_bet)]
cor_cut_df_bet <- cor(cut_df_bet)

cut_df_clos <- df[row.names(cent_net_clos)]
cor_cut_df_clos <- cor(cut_df_clos)

sel_measure_degree <- qgraph(cor_cut_df_degree, layout = "spring", labels = colnames(cor_cut_df_degree), theme="TeamFortress", title = paste("Network of the top", top_number, "nodes with the highest Degree"))

sel_measure_bet <- qgraph(cor_cut_df_bet, layout = "spring", labels = colnames(cor_cut_df_bet), theme="TeamFortress", title = paste("Network of the top", top_number, "nodes with the highest Betweenness"))

sel_measure_clos <- qgraph(cor_cut_df_clos, layout = "spring", labels = colnames(cor_cut_df_clos), theme="TeamFortress", title = paste("Network of the top", top_number, "nodes with the highest Closeness"))
  

  return(list(df = ndf, network =  qg, selected_bet = sel_measure_bet, selected_clos = sel_measure_clos, measures = cent_net, selected_degree = cent_net_degree, selected_betweenness = cent_net_bet, selected_closeness = cent_net_clos))
} 




FR_net_by_scales_top_measure <- function(df, list_cols, measure, top_number) # list_cols may have format: names = range (e.g.: cesd = 35:54)
{ measure <- tolower(measure)
  #unlisting cols to subset them
  vec_cols <- unlist(list_cols)
  #str_cols <- as.character(lapply(list_cols, function(x) x -  (min(unlist(list_cols)) - 1)))
  #subsetting
  ndf <- df[vec_cols]

  #creating correlation
  cor_mat <- cor(ndf)
  # creating indices to group by name

  
  
    update_indices <- function(indices, offset) {
    return(seq(from = 1 + offset, to = length(indices) + offset))
  }
  
  # Calculate the offset
  offset <- 0

  # Create the updated list of ranges
  updated_list_cols <- list()
  for (name in names(list_cols)) {
    updated_list_cols[[name]] <- update_indices(list_cols[[name]], offset)
    offset <- offset + length(list_cols[[name]])}
  
  
  # creating network  
qg <- qgraph(cor_mat, layout="spring", labels = colnames(cor_mat), groups = updated_list_cols ,color = sample(colors(), length(list_cols)))

    
cent_net <- as.data.frame(centrality(qg)) 
cent_net <- cent_net%>%
  arrange(case_when(
      measure == "outdegree" ~ desc(OutDegree),
      measure == "betweenness" ~ desc(Betweenness),
      measure == "closeness" ~ desc(Closeness)
    ))
cent_net <- cent_net[1:top_number, ]

# Subsetting the top variables
cut_df <- df[row.names(cent_net)]
cor_cut_df <- cor(cut_df)

sel_measure <- qgraph(cor_cut_df, layout = "spring", labels = colnames(cor_cut_df), theme="TeamFortress", title = paste("Network of the top", top_number, "nodes with the highest", measure))
  
  #qgraph(symp_zeroorder, layout="spring", labels = colnames(symp_zeroorder), color = sample(colors(), length(list_cols)), theme="TeamFortress", height = 180, width = 140, vsize=4)
  return(list(df = ndf, network =  qg, selected_network = sel_measure, selected_measures = cent_net))
}  

#test <- FR_net_by_scales_top_measure(df, list( Depr_cesd = 34:53, Depr_phq = 54:63, Depr_promis = 64:91, Depr_qids = 92:108), measure = 'closeness', top_number =  10)


aaa <- function(list_groups){update_indices <- function(indices, offset) {return(seq(from = 1 + offset, to = length(indices) + offset))}
  
  # Calculate the offset
  offset <- 0

  # Create the updated list of ranges
  updated_list_cols <- list()
  for (name in names(list_cols)) {
    updated_list_cols[[name]] <- update_indices(list_cols[[name]], offset)
    offset <- offset + length(list_cols[[name]])}}

```

# Network analysis of Depression and Anxiety Symptomatology

[Reference
article](https://www.frontiersin.org/journals/psychology/articles/10.3389/fpsyg.2018.01742/full "Visualizing Psychological Networks: A Tutorial in R")

## Packages and loading

```{r packages, message=FALSE}
library(dplyr)
#library(igraph)
#library(igraphdata)
library(qgraph)
#library(bootnet)
#library(corpcor)
#library(usethis)
library(MPsychoR)
library(openxlsx)
library(ggplot2)
library(tidyr)
#library(png)
#library(gridExtra)
library(smacof)

```

```{r}
df <- read.csv('../data/data_cleaned.csv')[2:215]


```

## Grouping variables

Ids = 1, Sociodem = 2:8, Pers_BFI2 = 9:23, Pers_hexaco = 24:33,
Depr_cesd = 34:53, Depr_phq = 54:63, Depr_promis = 64:91, Depr_qids =
92:108, Depr_Ans_dass = 108:128, Depr_Ans_hads = 129:142, Ans_gad =
143:149, Ans_tmas = 150:199, Ans_sas = 200:214

```{r}
groups_all_variables <- list(Ids = 1, Sociodem = 2:8, Pers_BFI2 = 9:23, Pers_hexaco = 24:33, Depr_cesd = 34:53, Depr_phq = 54:63, Depr_promis = 64:91, Depr_qids = 92:108, Depr_Ans_dass = 108:128, Depr_Ans_hads = 129:142, Ans_gad = 143:149, Ans_tmas = 150:199, Ans_sas = 200:214)

groups_all_scales <- list(Pers_BFI2 = 9:23, Pers_hexaco = 24:33, Depr_cesd = 34:53, Depr_phq = 54:63, Depr_promis = 64:91, Depr_qids = 92:108, Depr_Ans_dass = 108:128, Depr_Ans_hads = 129:142, Ans_gad = 143:149, Ans_tmas = 150:199, Ans_sas = 200:214)

groups_anx_dep <- list(Depr_cesd = 34:53, Depr_phq = 54:63, Depr_promis = 64:91, Depr_qids = 92:108, Depr_Ans_dass = 108:128, Depr_Ans_hads = 129:142, Ans_gad = 143:149, Ans_tmas = 150:199, Ans_sas = 200:214)

groups_all_scales_adjusted <- list(Pers_BFI2 = 1:15, Pers_hexaco = 16:25, Depr_cesd = 26:45, Depr_phq = 46:55, Depr_promis = 56:83, Depr_qids = 84:100, Depr_Ans_dass = 101:121, Depr_Ans_hads = 122:135, Ans_gad = 136:142, Ans_tmas = 143:192, Ans_sas = 193:206)
  
groups_anx_dep_adjusted <- list(Depr_cesd = 1:20, Depr_phq = 21:30, Depr_promis = 31:58, Depr_qids = 59:75, Depr_Ans_dass = 76:95, Depr_Ans_hads = 96:109, Ans_gad = 110:116, Ans_tmas = 117:166, Ans_sas = 167:181)

```

## Force-directed plotting with Fruchterman–Reingold

Most studies on networks in psychopathology have used the
Fruchterman-Reingold (FR) algorithm to create graphs. This algorithm is
like setting up a system of balls connected by stretchy strings. The
strings pull connected balls closer, while the other balls push them
apart, resulting in a neat graph where nodes are well-spaced and edges
are evenly distributed.

Force-directed algorithms aim to produce visually pleasing graphs by
minimizing edge crossings and spacing nodes evenly. The goal is not to
place the nodes in specific meaningful locations, but to make the
network easy to view, showing connections and clusters clearly.

It's important to avoid interpreting the spatial positions of nodes in
these graphs, as the placement is not meant to convey specific meanings.
Misinterpreting the layout is a common mistake, as it's natural to want
to find meaning in the arrangement.

The FR algorithm is the default in the qgraph R package, making it
straightforward to use.

### Creating individual scales networks using FR algorithm

These individual networks sho the connetions between the items.

```{r}


group_names <- c("Ids", "Sociodem", "Pers_BFI2", "Pers_hexaco", "Depr_cesd", "Depr_phq", "Depr_promis", "Depr_qids", "Depr_Ans_dass", "Depr_Ans_hads", "Ans_gad", "Ans_tmas", "Ans_sas")

n <- 3
for(sc in groups_all_scales){
  zero_order <- cor(df[sc])
  qgraph(zero_order, layout="spring", labels = colnames(zero_order), color = sample(colors(), 1), theme="TeamFortress", height = 180, width = 140, title = paste("Network of", group_names[n]))
  n <- n + 1
}


```

### All the scales

```{r, fig.height=10, fig.width=10}




color_nodes <- c("darkgreen", "lightgreen", "deepskyblue", "dodgerblue", "royalblue", "navy", "darkorange", "orange", "lightcoral", "firebrick", "darkred")


gen_zeroorder <- cor(df[9:214])

tt <-qgraph(gen_zeroorder, layout="spring", labels = colnames(gen_zeroorder), groups = groups_all_scales_adjusted , color = color_nodes, theme="TeamFortress", height = 180, width = 140, vsize=3)


```

```{r}
clustcoef_auto(tt)

clusteringPlot(tt)
```

```{r}
phq <- df[54:63]
cor_phq <- cor_auto(phq)


q_phq <- qgraph(cor_phq)

clustcoef_auto(q_phq)

clusteringPlot(q_phq)
```

### Only the scales related to anxiety and depression

```{r, fig.height=10, fig.width=10}


color_nodes_anx_dep <- c("deepskyblue", "dodgerblue", "royalblue", "navy", "darkorange", "orange", "lightcoral", "firebrick", "darkred")


symp_zeroorder <- cor(df[34:214])
anx_dep_FR <- qgraph(symp_zeroorder, layout="spring", labels = colnames(symp_zeroorder), groups = groups_anx_dep_adjusted , color = color_nodes_anx_dep, theme="TeamFortress", label.prop=0.6, vsize=1)


```

Absolute Node Strength in Order of Strength takes absolute values and
Influence consider the negative values

```{r}

anx_dep_FR_cent_abs <- as.data.frame(centrality(anx_dep_FR))

anx_dep_FR_cent_abs_strength <- anx_dep_FR_cent_abs %>%
arrange(desc(OutDegree)) %>%
select(Strength = OutDegree, Betweenness, Closeness, Influence = InExpectedInfluence)

anx_dep_FR_cent_abs_strength
```


En redes convencionales, los bordes suelen tener solo pesos positivos, pero en redes psicológicas, los bordes pueden ser negativos, indicando relaciones inversas entre variables (por ejemplo, más café = peor calidad de sueño).

Una forma común de manejar estos pesos negativos es tomar el valor absoluto, tratándolos como positivos para calcular métricas como fuerza de nodo, cercanía e intermediación. Sin embargo, algunas métricas, como la influencia esperada, permiten que los bordes negativos y positivos se cancelen entre sí, lo cual es útil cuando los nodos no se pueden recodificar, como en redes de síntomas, donde los valores altos indican peor sintomatología.

```{r}

to_del <- c("dass_06", "dass_08", "dass_14", "phq_10", "dass_01", "dass_11", "dass_12", "dass_18")

df_n <- df[, -which(names(df) %in% to_del)]


symp_zeroorder <- cor_auto(df_n[34:206])

# 1. Convert the correlation matrix into an adjacency matrix
adj_matrix <- as.matrix(symp_zeroorder)

# Optional: Apply a threshold to binarize the matrix (only keep strong correlations)
#adj_matrix[abs(adj_matrix) < 0.3] <- 0  # Set a threshold of 0.3 (or adjust as needed)

# attribute abs values to negative edges
adj_matrix[adj_matrix < 0] <- abs(adj_matrix[adj_matrix < 0])

# 2. Convert the adjacency matrix to an igraph object
graph_symp <- graph.adjacency(adj_matrix, mode = "undirected", weighted = TRUE, diag = FALSE)

# 3. Run the Louvain algorithm to detect communities
louvain_communities <- cluster_louvain(graph_symp)

# 4. Print the community memberships
membership(louvain_communities)


#plot(graph_symp, vertex.color=membership(louvain_communities))
plot(graph_symp, vertex.color=membership(louvain_communities), layout=layout_nicely(graph_symp), vertex.size=5, vertex.shape="sphere", edge.width=2, edge.arrow=TRUE)

louvain_communities$modularity

groups(louvain_communities)
```
> louvain_communities$modularity
[1] 0.02214074 0.02229915
> 
> groups(louvain_communities)
$`1`
 [1] "cesd_01" "cesd_11" "cesd_12" "cesd_13" "cesd_15" "cesd_18" "qids_03" "qids_04" "qids_06" "qids_08" "qids_12"
[12] "qids_14" "qids_15" "dass_02" "dass_04" "dass_07" "dass_09" "dass_15" "dass_19" "dass_20" "hads_03" "hads_08"
[23] "hads_09" "hads_13" "hads_14" "gad_07"  "tmas_02" "tmas_03" "tmas_04" "tmas_08" "tmas_15" "tmas_16" "tmas_41"
[34] "tmas_48" "sas_02"  "sas_04"  "sas_05"  "sas_08"  "sas_09"  "sas_10"  "sas_11"  "sas_12"  "sas_14"  "sas_15" 

$`2`
 [1] "cesd_02"   "cesd_03"   "cesd_04"   "cesd_06"   "cesd_07"   "cesd_08"   "cesd_09"   "cesd_10"   "cesd_14"  
[10] "cesd_16"   "cesd_17"   "cesd_20"   "phq_01"    "phq_02"    "phq_04"    "phq_05"    "phq_06"    "phq_07"   
[19] "phq_08"    "phq_09"    "promis_01" "promis_02" "promis_03" "promis_04" "promis_05" "promis_06" "promis_07"
[28] "promis_08" "promis_09" "promis_10" "promis_11" "promis_12" "promis_13" "promis_14" "promis_15" "promis_16"
[37] "promis_17" "promis_18" "promis_19" "promis_20" "promis_21" "promis_22" "promis_23" "promis_24" "promis_25"
[46] "promis_26" "promis_27" "promis_28" "qids_05"   "qids_10"   "qids_11"   "qids_13"   "dass_03"   "dass_05"  
[55] "dass_10"   "dass_13"   "dass_16"   "dass_17"   "dass_21"   "hads_02"   "hads_04"   "hads_06"   "hads_12"  
[64] "tmas_01"   "tmas_26"   "tmas_36"   "tmas_46"   "tmas_49"  

$`3`
 [1] "cesd_05" "cesd_19" "phq_03"  "qids_01" "qids_02" "qids_07" "qids_09" "qids_16" "hads_01" "hads_05" "hads_07"
[12] "hads_10" "hads_11" "gad_01"  "gad_02"  "gad_03"  "gad_04"  "gad_05"  "gad_06"  "tmas_05" "tmas_06" "tmas_07"
[23] "tmas_09" "tmas_10" "tmas_11" "tmas_12" "tmas_13" "tmas_14" "tmas_17" "tmas_18" "tmas_19" "tmas_20" "tmas_21"
[34] "tmas_22" "tmas_23" "tmas_24" "tmas_25" "tmas_27" "tmas_28" "tmas_29" "tmas_30" "tmas_31" "tmas_32" "tmas_33"
[45] "tmas_34" "tmas_35" "tmas_37" "tmas_38" "tmas_39" "tmas_40" "tmas_42" "tmas_43" "tmas_44" "tmas_45" "tmas_47"
[56] "tmas_50" "sas_01"  "sas_03"  "sas_06"  "sas_07"  "sas_13" 

### Density, bridge centrality and smallworldness
```{r}


plot(louvain_communities, graph_symp)


# Density
mean(adj_matrix[lower.tri(adj_matrix)]) 

#N of edges
sum(adj_matrix[lower.tri(adj_matrix)]) 

# N of nodes
ncol(adj_matrix)

# bridge centralities
bridge(graph_symp, communities = louvain_communities, useCommunities =  c("1","2", "3"))

#$transitivity: clustering coefficient (not very good for weighted networks)
#APL: average of all shortest path lengths

smallworldIndex(qgraph(adj_matrix))

```

```{r}
#group_1 <- c("cesd_01", "cesd_15", "cesd_18", "qids_03", "qids_04", "qids_06", 
             "qids_08", "qids_12", "qids_14", "qids_15", "dass_02", "dass_03", 
             "dass_04", "dass_06", "dass_07", "dass_08", "dass_09", "dass_14", 
             "dass_15", "dass_19", "dass_20", "hads_03", "hads_08", "hads_09", 
             "hads_13", "hads_14", "gad_07", "tmas_02", "tmas_03", "tmas_16", 
             "tmas_27", "tmas_41", "tmas_44", "tmas_48", "sas_02", "sas_04", 
             "sas_05", "sas_08", "sas_09", "sas_10", "sas_11", "sas_12", 
             "sas_14", "sas_15")

# Group 2
#group_2 <- c("cesd_02", "cesd_03", "cesd_04", "cesd_06", "cesd_07", "cesd_08", 
             "cesd_09", "cesd_10", "cesd_11", "cesd_12", "cesd_13", "cesd_14", 
             "cesd_16", "cesd_17", "cesd_20", "phq_01", "phq_02", "phq_04", 
             "phq_05", "phq_06", "phq_07", "phq_08", "phq_09", "phq_10", 
             "promis_01", "promis_02", "promis_03", "promis_04", "promis_05", 
             "promis_06", "promis_07", "promis_08", "promis_09", "promis_10", 
             "promis_11", "promis_12", "promis_13", "promis_14", "promis_15", 
             "promis_16", "promis_17", "promis_18", "promis_19", "promis_20", 
             "promis_21", "promis_22", "promis_23", "promis_24", "promis_25", 
             "promis_26", "promis_27", "promis_28", "qids_05", "qids_10", 
             "qids_11", "qids_13", "dass_05", "dass_10", "dass_13", "dass_16", 
             "dass_17", "dass_21", "hads_02", "hads_04", "tmas_36", "tmas_46", 
             "tmas_49")

# Group 3
#group_3 <- c("cesd_05", "cesd_19", "phq_03", "qids_01", "qids_02", "qids_07", 
             "qids_09", "qids_16", "dass_01", "dass_11", "dass_12", "dass_18", 
             "hads_01", "hads_05", "hads_06", "hads_07", "hads_10", "hads_12", 
             "gad_01", "gad_02", "gad_03", "gad_04", "gad_05", "gad_06", 
             "tmas_01", "tmas_04", "tmas_05", "tmas_06", "tmas_07", "tmas_08", 
             "tmas_09", "tmas_10", "tmas_11", "tmas_12", "tmas_13", "tmas_14", 
             "tmas_15", "tmas_17", "tmas_18", "tmas_19", "tmas_20", "tmas_21", 
             "tmas_22", "tmas_23", "tmas_24", "tmas_25", "tmas_26", "tmas_28", 
             "tmas_29", "tmas_30", "tmas_31", "tmas_32", "tmas_33", "tmas_34", 
             "tmas_35", "tmas_37", "tmas_38", "tmas_39", "tmas_40", "tmas_42", 
             "tmas_43", "tmas_45", "tmas_47", "tmas_50", "sas_01", "sas_03", 
             "sas_06", "sas_07", "sas_13")

# Group 4
#group_4 <- c("hads_11")
```



```{r}

# Group 1
group_1 <- c("cesd_01", "cesd_18", "qids_03", "qids_06", "qids_08", "qids_15", 
             "dass_02", "dass_04", "dass_07", "dass_09", "dass_15", "dass_19", 
             "dass_20", "hads_03", "hads_08", "hads_09", "hads_13", "hads_14", 
             "gad_07", "tmas_02", "tmas_03", "tmas_04", "tmas_08", "tmas_15", 
             "tmas_16", "tmas_36", "tmas_41", "tmas_48", "sas_02", "sas_04", 
             "sas_05", "sas_08", "sas_09", "sas_10", "sas_11", "sas_12", 
             "sas_14", "sas_15")

# Group 2
group_2 <- c("cesd_02", "cesd_03", "cesd_04", "cesd_06", "cesd_07", "cesd_08", 
             "cesd_09", "cesd_10", "cesd_11", "cesd_12", "cesd_14", "cesd_15", 
             "cesd_16", "cesd_17", "cesd_20", "phq_01", "phq_02", "phq_04", 
             "phq_05", "phq_06", "phq_07", "phq_08", "phq_09", "promis_01", 
             "promis_02", "promis_03", "promis_04", "promis_05", "promis_06", 
             "promis_07", "promis_08", "promis_09", "promis_10", "promis_11", 
             "promis_12", "promis_13", "promis_14", "promis_15", "promis_16", 
             "promis_17", "promis_18", "promis_19", "promis_20", "promis_21", 
             "promis_22", "promis_23", "promis_24", "promis_25", "promis_26", 
             "promis_27", "promis_28", "qids_04", "qids_05", "qids_10", 
             "qids_11", "qids_12", "qids_13", "qids_14", "dass_03", "dass_05", 
             "dass_10", "dass_13", "dass_16", "dass_17", "dass_21", "hads_02", 
             "hads_04", "hads_06", "hads_12", "tmas_01", "tmas_26", "tmas_46", 
             "tmas_49")

# Group 3
group_3 <- c("cesd_05", "cesd_13", "cesd_19", "phq_03", "qids_01", "qids_02", 
             "qids_07", "qids_09", "qids_16", "hads_01", "hads_05", "hads_07", 
             "hads_10", "hads_11", "gad_01", "gad_02", "gad_03", "gad_04", 
             "gad_05", "gad_06", "tmas_05", "tmas_06", "tmas_07", "tmas_09", 
             "tmas_10", "tmas_11", "tmas_12", "tmas_13", "tmas_14", "tmas_17", 
             "tmas_18", "tmas_19", "tmas_20", "tmas_21", "tmas_22", "tmas_23", 
             "tmas_24", "tmas_25", "tmas_27", "tmas_28", "tmas_29", "tmas_30", 
             "tmas_31", "tmas_32", "tmas_33", "tmas_34", "tmas_35", "tmas_37", 
             "tmas_38", "tmas_39", "tmas_40", "tmas_42", "tmas_43", "tmas_44", 
             "tmas_45", "tmas_47", "tmas_50", "sas_01", "sas_03", "sas_06", 
             "sas_07", "sas_13")



communities_df <- as.data.frame(c(df_n[group_1], df_n[group_2], df_n[group_3]))

#all_grp <- list(group_1, group_2, group_3)


cat(length(group_1), length(group_2), length(group_3))





#grps <- list(group_1 = 1:l1, group_2 = l1+1:l2, group_3 = l2 +1:l3, group_4)

grps <- list(group_1 = 1:38, group_2 = 39:111, group_3 = 112:173)





symp_zeroorder_com <- cor_auto(communities_df)

anx_dep_FR <- qgraph(symp_zeroorder, layout="spring", labels = colnames(symp_zeroorder_com), groups = grps , color = c("pink", "navy", "darkorange", "darkred"), theme="TeamFortress", label.prop=0.6, vsize=1)

```

```{r}

library(networktools)
bridge_centrality <- bridge(symp_zeroorder, communities = groups_anx_dep_adjusted)

# View the bridge centrality results
bridge_st <- as.data.frame(bridge_centrality$`Bridge Strength`)
bridge_bet <- as.data.frame(bridge_centrality$`Bridge Betweenness`)
bridge_clo <- as.data.frame(bridge_centrality$`Bridge Closeness`)
#as.data.frame(bridge_centrality$communities)

bridge_bet

bridge_st %>%
  arrange(desc(bridge_centrality$`Bridge Strength`)) 

bridge_bet %>%
  arrange(desc(bridge_centrality$`Bridge Betweenness`)) #%>%

bridge_clo %>%
  arrange(bridge_centrality$`Bridge Closeness`) #%>%
  

```

TOP 3 Bridge Strength: Estas medidas evalúan el número y la fuerza de
las conexiones entre un nodo y nodos en diferentes clústeres. Una alta
fuerza de puente o influencia esperada de puente sugiere que un nodo
desempeña un papel significativo en la conexión de diferentes
comunidades dentro de la red.

phq_02 108.969294 - Sentirse desanimado/a, deprimido/a o sin esperanza
phq_06 108.763934 - Sentirse mal consigo mismo/a o sentirse fracasado/a,
o pensar que se ha decepcionado a sí mismo/a o a los que le rodean\
gad_04 108.318513 - Ha tenido dificultad para relajarse

TOP 3 Bridge Betweenness: Esta medida examina la frecuencia con que un
nodo se encuentra en el camino más corto entre dos nodos de diferentes
clústeres. Un alto betweenness de puente indica que el nodo actúa como
un puente crucial, canalizando el flujo de información o influencia
entre esas comunidades.

tmas_26 289 - Tengo plena confianza en mí mismo/a tmas_25 138 - A menudo
tengo miedo de ruborizarme tmas_22 111 - Me despierto frecuentemente y
no descanso bien

TOP 3 Bridge Closeness: Esta medida cuantifica la facilidad con que un
nodo puede alcanzar todos los nodos pertenecientes a otros clústeres.
Una alta cercanía de puente implica que un nodo puede influenciar o ser
influenciado por nodos en diferentes clústeres con relativa facilidad.

tmas_49 Creo que no soy más nervioso/a que los demás
tmas_08 Nunca me ruborizo
tmas_36 No me ruborizo con más frecuencia que otros/as


tmas_07 0.6086924 - La vida es una constante fatiga para mí tmas_44
0.6076168 - No puedo concentrarme en nada qids_05 0.5955376 - Sentirse
triste

By Betweenness

```{r}
anx_dep_FR_cent_abs <- as.data.frame(centrality(anx_dep_FR))

anx_dep_FR_cent_abs_strength <- anx_dep_FR_cent_abs %>%
arrange(desc(Betweenness)) %>%
select(Betweenness, Strength = OutDegree, Closeness, Influence = InExpectedInfluence)

anx_dep_FR_cent_abs_strength
```

By Closeness

```{r}
anx_dep_FR_cent_abs <- as.data.frame(centrality(anx_dep_FR))

anx_dep_FR_cent_abs_strength <- anx_dep_FR_cent_abs %>%
arrange(desc(Closeness)) %>%
select(Closeness, Strength = Betweenness,OutDegree, Influence = InExpectedInfluence)

anx_dep_FR_cent_abs_strength
```

```{r}
clustcoef_auto(anx_dep_FR)
```

```{r}

# Defina o número de nós (n) e a probabilidade de conexão (p)
n <- 181
p <- 0.2

# Gere uma rede aleatória usando o modelo Erdös-Rényi G(n, p)
random_network <- erdos.renyi.game(n, p, directed = FALSE)

# Visualize a rede
plot(random_network)

#bridge(random_network, communities = 5)

# Detect communities using the Louvain method
louvain_communities <- cluster_louvain(random_network)

# Print the community memberships
membership(louvain_communities)




```

```{r}
clusteringPlot(anx_dep_FR)
```

```{r}
# Load necessary libraries
library(igraph)
library(qgraph)

symp_zeroorder <- cor_auto(df[34:214])

# Assuming symp_zeroorder is an adjacency matrix or a correlation matrix
# Convert the matrix to an igraph object
graph_symp <- graph_from_adjacency_matrix(symp_zeroorder, mode = "undirected", weighted = TRUE, diag = FALSE)

# Detect communities using Louvain
communities <- cluster_louvain(graph_symp)

# Now, visualize the network with the identified clusters using qgraph
qgraph(symp_zeroorder, groups = communities$membership, layout = "spring")

transitivity(graph_symp, type = "local")

library(NetworkToolbox)

dm <- depend(df[34:214])

clustcoeff(dm, weighted = T)
```

```{r}
smallworldness(symp_zeroorder)

```

```{r}
#lower.tri(symp_zeroorder)

centralityPlot(anx_dep_FR)

bridges(symp_zeroorder)
```

### Networks of the top n measures of centrality

#### All Scales

Let's explore measures of centrality such as Strength (Degree),
Betweenness and Closeness by sorting the all top results for each
measure and creating a Network for each of them.

```{r}
all_cent_measures_25_top <- FR_net_by_scales_topnum_measures(df, list(Sociodem = 2:8, Pers_BFI2 = 9:23, Pers_hexaco = 24:33, Depr_cesd = 34:53, Depr_phq = 54:63, Depr_promis = 64:91, Depr_qids = 92:108, Depr_Ans_dass = 108:128, Depr_Ans_hads = 129:142, Ans_gad = 143:149, Ans_tmas = 150:199, Ans_sas = 200:214), 50)

cor_mat <- cor(df[2:214])
all_data_qg <- qgraph(cor_mat, layout="spring", labels = colnames(cor_mat), groups = groups_all_scales_adjusted ,color = color_nodes, title = "Network of all scales", theme="TeamFortress")


all_data_qg_cent <- centrality(all_data_qg)
all_data_qg_cent <- as.data.frame(all_data_qg_cent)

all_data_qg_cent_strength <- all_data_qg_cent %>%
arrange(desc(OutDegree)) %>%
select(Strength = OutDegree, Betweenness, Closeness, Influence = InExpectedInfluence)



round(all_cent_measures_25_top$selected_closeness[1:5],5)

#all_data_qg
#row.names(all_cent_measures_25_top$selected_degree)
```

#####Strength

It is strength due to the fact that the connection between nodes used is
a correlation zero-order matrix, thus a weight matrix. Therefore,
Strength is the sum of the correlations of one node to all other nodes
with higher values reflecting greater centrality in the network (Cai et
al., 2022). There is a remarkable dominance of promis items among the
strongest ones. All of them are arguably constructs of depressed mood.

promis_28: Me sentí completamente agotado/a emocionalmente -\> Humor
deprimido promis_05: Sentí que nada me podía animar -\> Anhedonia /
Humor deprimido promis_15: Me sentí deprimido/a -\> Humor deprimido
promis_21: Me sentí desesperanzado/a -\> Humor deprimido promis_07: Me
sentí triste -\> Humor deprimido

```{r}
all_data_qg_cent_strength <- all_data_qg_cent %>%
arrange(desc(OutDegree)) %>%
select(Strength = OutDegree, Betweenness, Closeness, Influence = InExpectedInfluence)

all_data_qg_cent_strength
all_data_qgplot_cent_strength <- ggplot(all_data_qg_cent_strength, aes(Strength)) + geom_boxplot(color="darkblue",fill="lightblue",  outlier.colour = "red", show.legend = TRUE) + labs(title = "Strength of All items", x="Strength")

ggsave('../images/all_data_qgplot_cent_strength.png', all_data_qgplot_cent_strength)
```

#####Betweenness

A node with high betweenness is a node that tends to connect clusters of
nodes together (Deserno et al., 2022). The item 10 from BFI-2 is by far
the one that seems to be more able to connect different clusters. As it
is about having energy (or lacking it), it seems plausible to
hypothetize that the energy level is a component that interconnects
clusters of symptoms.

bfi2_10: Lleno/a de energía tmas_26. Tengo plena confianza en mí mismo/a
bfi2_12: Que tiende a sentirse deprimido/a, melancólico/a hads_13: Me
asaltan sentimientos repentinos de pánico qids_12: Pensamientos sobre la
muerte o el suicidio

```{r}
all_data_qg_cent_betweenness <- all_data_qg_cent %>%
arrange(desc(Betweenness)) %>%
select(Betweenness, Strength = OutDegree, Closeness, Influence = InExpectedInfluence)

all_data_qg_cent_betweenness
all_data_qgplot_cent_betweenness <- ggplot(all_data_qg_cent_betweenness, aes(Betweenness)) + geom_boxplot(color="darkblue",fill="lightblue",  outlier.colour = "red", show.legend = TRUE) + labs(title = "Betweenness of All items", x="Betweenness")

ggsave('../images/all_data_qgplot_cent_betweenness.png', all_data_qgplot_cent_betweenness)
```

#####Closeness

Closeness quantifies how far removed a node is from every other node in
the network (Deserno et al., 2022). As in Strength, there is a dominance
of promis items among the ones that are more influential on closeness.
Also, all of them seem to be constructs of depressed mood.

promis_28: Me sentí completamente agotado/a emocionalmente -\> Humor
deprimido promis_05: Sentí que nada me podía animar -\> Anhedonia /
Humor deprimido promis_07: Me sentí triste -\> Humor deprimido
promis_21: Me sentí desesperanzado/a -\> Humor deprimido promis_15: Me
sentí deprimido/a -\> Humor deprimido

```{r}
all_data_qg_cent_closeness <- all_data_qg_cent %>%
arrange(desc(Closeness)) %>%
select(Closeness, Strength = OutDegree, Betweenness, Influence = InExpectedInfluence)

all_data_qg_cent_closeness
all_data_qgplot_cent_closeness <- ggplot(all_data_qg_cent_closeness, aes(Closeness)) + geom_boxplot(color="darkblue",fill="lightblue",  outlier.colour = "red", show.legend = TRUE) + labs(title = "Closeness of All items", x="Closeness")

ggsave('../images/all_data_qgplot_cent_closeness.png', all_data_qgplot_cent_closeness)
```

#### Depression and Anxiety Scales

```{r}
anx_dep_cent_measures_25_top <- FR_net_by_scales_topnum_measures(df, list(Depr_cesd = 34:53, Depr_phq = 54:63, Depr_promis = 64:91, Depr_qids = 92:108, Depr_Ans_dass = 108:128, Depr_Ans_hads = 129:142, Ans_gad = 143:149, Ans_tmas = 150:199, Ans_sas = 200:214), 10)

anx_dep_cent_measures_25_top$selected_degree[1:5]
anx_dep_cent_measures_25_top$selected_betweenness[1:5]
anx_dep_cent_measures_25_top$selected_closeness[1:5]
```

```{r, fig.height=20}
centralityPlot(symp_zeroorder, scale = "raw0", include = c("Strength", 
"Closeness", "Betweenness", "ExpectedInfluence"))
```

#### Escalas de Ansiedad y depresión

### Removing most influential nodes

#### Closeness

#### Betweenness

#### Degree

#### Progressive construccion of the network

By joining step by step

## Multidimensional Scaling (MDS) of Networks

MDS represents proximities among variables as distances between points
in a low-dimensional space (e.g., two or three dimensions; Mair et al.,
2016). Proximity is an umbrella term for “similarities” between
variables (e.g., correlation) or “dissimilarities” (e.g., Euclidean
distance). Because MDS helps represent complex data in low-dimensional
space, it dovetails precisely with the goal of visual presentation of
complex psychological networks. That is, we can use MDS to represent
proximities in a two-dimensional space (e.g., X & Y) to produce
two-dimensional network plots. MDS is particularly useful for
understanding networks because the distances between plotted nodes are
interpretable as Euclidean distances.

Because the smacof R package (De Leeuw and Mair, 2009) requires
dissimilarities (rather than similarities) as input, we will convert the
correlation matrix into a dissimilarity matrix.

```{r}
groups <- list(Pers_BFI2 = 9:23, Pers_hexaco = 24:33, Depr_cesd = 34:53, Depr_phq = 54:63, Depr_promis = 64:91, Depr_qids = 92:108, Depr_Ans_dass = 108:128, Depr_Ans_hads = 129:142, Ans_gad = 143:149, Ans_tmas = 150:199, Ans_sas = 200:214)

n <- 3
for(sc in groups){
  zero_order_md <- cor(df[sc])
  qgraph(zero_order_md, layout="spring", labels = colnames(zero_order_md), color = sample(colors(), 1), theme="TeamFortress", height = 180, width = 140, title = paste("MDS Network of", group_names[n]))
  n <- n + 1
}

```

### Transformations

Shepard diagrams allow us to visualize how well our MDS configuration
fits our dissimilarity matrix. When the dissimilarities align in a
linear fashion, a ratio or interval MDS is most appropriate. In other
cases, a nonlinear transformation such as ordinal MDS or spline MDS may
be more appropriate. The normalized stress values (plotted in each
graph) can help guide us in deciding which transformation provides the
best fit.

#### Shepard diagrams for all scales

It's possible to see that Spline and Ordinal MDS are the transformations
with less stress, with the later showing a slightly better result.

```{r}

gen_zeroorder <- cor(df[9:214])

dissimilarities <- sim2diss(gen_zeroorder)

MDS_ordinal <- mds(dissimilarities, type = 'ordinal')
plot(MDS_ordinal, plot.type = "Shepard", main = "Ordinal")
text(1.1,0.3, paste("Stress =", round(MDS_ordinal$stress,2)))

MDS_ratio <- mds(dissimilarities, type = "ratio")
plot(MDS_ratio, plot.type = "Shepard", main = "Ratio")
text(1.1,0.3, paste("Stress =", round(MDS_ratio$stress,2)))

MDS_interval <- mds(dissimilarities, type = "interval")
plot(MDS_interval, plot.type = "Shepard", main = "Interval")
text(1.1,0.3, paste("Stress =", round(MDS_interval$stress,2)))

MDS_mspline <- mds(dissimilarities, type = "mspline")
plot(MDS_mspline, plot.type = "Shepard", main = "Spline")
text(1.1,0.3, paste("Stress =", round(MDS_mspline$stress,2)))
```

#### All the scales with MDS Ordinal transformation

```{r}


groups <- list(Pers_BFI2 = 1:15, Pers_hexaco = 16:25, Depr_cesd = 26:45, Depr_phq = 46:55, Depr_promis = 56:83, Depr_qids = 84:100, Depr_Ans_dass = 101:120, Depr_Ans_hads = 121:134, Ans_gad = 135:141, Ans_tmas = 142:191, Ans_sas = 192:206)


color_nodes <- c("darkgreen", "lightgreen", "deepskyblue", "dodgerblue", "royalblue", "navy", "darkorange", "orange", "lightcoral", "firebrick", "darkred")


gen_zeroorder <- cor(df[9:214])

qgraph(gen_zeroorder, layout=MDS_ordinal$conf, labels = colnames(gen_zeroorder), groups = groups , color = color_nodes, theme="TeamFortress", height = 180, width = 140, vsize=3)
```

#### Depression and anxiety scales with MDS Ordinal transformation

```{r}
dep_anx_mds_qg <- qgraph(symp_zeroorder, layout= MDS_ordinal$conf, labels = colnames(symp_zeroorder), groups = groups_anx_dep , color = color_nodes_anx_dep, theme="TeamFortress", vsize=2)

```

# From this point consider all a draft

### Centrality Measures on MDS (to continue...)

Let's explore the centrality. We order the items with the highest
outdegrees and, then, highest Betweenness. Outdegree in a correlation
matrix network could be defined as the sum of variable correlations that
have edges with a specific node. Due to the nature of the undirected
edges based on correlation matrices, outdegrees and indegrees are
redundant measures. In the code below we will identify the 50 most
influential nodes and build a matrix network with them.

```{r}

centrality_dep_anx_mds_qg <- centrality(dep_anx_mds_qg) 
  
centrality_dep_anx_mds_qg <- as.data.frame(centrality_dep_anx_mds_qg) %>%
arrange(desc(OutDegree), desc(Betweenness))

cent_dep_anx_mds_qg_50_degrees <- as.vector(rownames(centrality_dep_anx_mds_qg))[1:50]

sub_top50_degree_df <- df[cent_dep_anx_mds_qg_50_degrees]

sub_top50_degree_df_cor <- cor(sub_top50_degree_df)

diss_sub_top50_degree_df <- sim2diss(sub_top50_degree_df_cor)

MDS_ord_sub_top50_degree <- mds(dissimilarities, type = 'ordinal')


qgraph(sub_top50_degree_df_cor, layout= MDS_ord_sub_top50_degree$conf, labels = colnames(sub_top50_degree_df_cor),  vsize=4)


```

```{r}
z_central <- (centrality_dep_anx_mds_qg$OutDegree - mean(centrality_dep_anx_mds_qg$OutDegree)) / sd(centrality_dep_anx_mds_qg$OutDegree)
z_bet <- (centrality_dep_anx_mds_qg$Betweenness - mean(centrality_dep_anx_mds_qg$Betweenness)) / sd(centrality_dep_anx_mds_qg$Betweenness)
```

```{r}

mm_central <- ((centrality_dep_anx_mds_qg$OutDegree - min(centrality_dep_anx_mds_qg$OutDegree)) / (max(centrality_dep_anx_mds_qg$OutDegree) - min(centrality_dep_anx_mds_qg$OutDegree))) * 3

mm_bet <- ((centrality_dep_anx_mds_qg$Betweenness - min(centrality_dep_anx_mds_qg$Betweenness)) / (max(centrality_dep_anx_mds_qg$Betweenness) - min(centrality_dep_anx_mds_qg$Betweenness))) * 3
```

```{r}
plot_output <- centralityPlot(dep_anx_mds_qg)

plot_output + theme(plot.margin = margin(t = 0.1, r = 0.10, b = 0.10, l = 0.10, unit = "cm"), label.cex = 1)

ggsave("my_plot.png", plot_output, width = 10, height = 20, units = "in", limitsize = FALSE)

clusteringPlot(dep_anx_mds_qg)
```

```{r}
centrality_dep_anx_mds_qg <- centrality(dep_anx_mds_qg)

centrality_dep_anx_mds_qg <- as.data.frame(centrality_dep_anx_mds_qg) %>%
arrange(desc(OutDegree), desc(Betweenness))

centrality_dep_anx_mds_qg[1:5]
```

```{r, fig.width=15, fig.height=10}

qgraph(symp_zeroorder, layout= MDS_ordinal$conf, labels = colnames(symp_zeroorder), groups = groups_anx_dep , color = color_nodes_anx_dep, theme="TeamFortress", vsize=mm_central)

```

```{r}

```

```{r}

```

```{r}
bet_all_25top

mmdf <- as.data.frame(mm_bet) 
mmdf%>%
  arrange(desc(mmdf))
```

-   bfi2_10 Lleno/a de energía
-   tmas_26 Tengo plena confianza en mí mismo/a
-   bfi2_12 Que tiende a sentirse deprimido/a, melancólico/a

```{r, fig.height=10, fig.width=10}


bet_all_25top <- all_cent_measures_25_top$selected_betweenness[1:5]


gr <- row.names(bet_all_25top)

all_zeroorder <- cor(df[2:214])

qg_bet <- qgraph(all_zeroorder, layout="spring", labels = colnames(all_zeroorder), groups = list(bfi2_10 = 17, tmas_26 = 174, bfi2_12 = 19) , color = "darkgreen", theme="TeamFortress", vsize=3)

qb_bet <- centrality(qg_bet)

mm_bet <- ((qb_bet$Betweenness - min(qb_bet$Betweenness)) / (max(qb_bet$Betweenness) - min(qb_bet$Betweenness))) * 5


qgraph(all_zeroorder, layout="spring", groups = index_list , color = c(sample(colors(), length(index_list))), vsize=mm_bet, labels = FALSE)
```

```{r}
by_cent_measure_top10 <- FR_net_by_scales_topnum_measures(df, groups, 10) # groups is a list that has personality scales

by_cent_measure_top10$selected_

groups

nodes_by_metrics_all <- function(df, qg){
  all_zeroorder <- cor(df)
  
}
```

```{r}
```

```{r}

original <- read.xlsx('../data/data.xlsx')
original[c(10, 215, 13, 216, 16, 217, 21, 218, 25, 219, 27, 220, 28, 221, 30, 222, 31, 223, 33, 224, 150, 225, 153, 226, 154, 227, 157, 228, 164, 229, 165, 230, 166, 231, 175, 232, 185, 233, 195, 234, 196, 235, 198, 236)]
```

```{r}


original[225:236]


```
