---
title: "data_prep_processing"
author: "Pietro Olivetti"
date: "2024-07-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Questions:

-   Drop phq10?
- Hacer análisis exploratório para cada escala?
- reverse items, qué hacer?
  - Sería más lógico remplazar el elemento por su variable invertida

## Packages and loading


```{r}
library(dplyr)
library(qgraph)
library(openxlsx)
library(ggplot2)
library(tidyr)

if (!require(stringr)) install.packages('stringr')
library(stringr)

```

```{r}
df <- read.xlsx('data.xlsx')
head(df)
```

## Data Cleaning

### Identifying and removing missing values

```{r}

#Amount of NAs 
sum(is.na(df))

#subsetting them
showna <- df[!complete.cases(df) , ]

#Checking amount of missing values for each row
id.nas <- c(6, 255, 399, 552, 568, 672, 676, 831, 871)
c.nas <- c()

for (m in 1:dim(showna)[1]){
  c.nas <- append(c.nas, sum(is.na(showna[m , ])))
  }

missing_by_rows <- data.frame(ID = id.nas, NAs_number = c.nas)

missing_by_rows

# subsetting rows
df[c(id.nas),]

dim(df)
```

Most of the NAs are for civil status. As there are only few of them, these rows will be removed from the dataset.

```{r}
df <- df[ - c(id.nas),]
sum(is.na(df))
```

## Data Transformation

### Age
Age type is character, so we'll change it to numeric and look for invalid values or NAs.
The following invalid characters were found: "1994" ".3"   "&6"   "6"    "5&"  
We imputed medians on the NAs and 30 when the Year of birth was indicated

```{r}
typeof(df$Age)

# Regular expression to match exactly two digits
pattern <- "^\\d{2}$"
# Identify non-matching values
non_matching <- df[!str_detect(df$Age, pattern), ]
non_matching

# One had 1994 so we replace with 30 and the others with the median age (46) on character
df[105,5] <- 30

df <- df %>% 
  mutate(Age = as.numeric(Age)) %>%
  mutate(Age = ifelse(Age > 100 | Age < 18, median(Age, na.rm = TRUE), Age)) %>%
  mutate(Age = ifelse(is.na(Age), median(Age, na.rm = TRUE), Age))


# Are there NAs  
sum(is.na(df))




```


### PHQ items

The domain here is 1 to 4 but the study of reference has it as 0 to 3. Recoding the points.

```{r}

df_transf <- df %>% 
  mutate(phq_01 = recode(phq_01, `4` = 3, `3` = 2, `2` = 1, `1`= 0)) %>%
  mutate(phq_02 = recode(phq_02, `4` = 3, `3` = 2, `2` = 1, `1`= 0)) %>%
  mutate(phq_03 = recode(phq_03, `4` = 3, `3` = 2, `2` = 1, `1`= 0)) %>%
  mutate(phq_04 = recode(phq_04, `4` = 3, `3` = 2, `2` = 1, `1`= 0)) %>%
  mutate(phq_05 = recode(phq_05, `4` = 3, `3` = 2, `2` = 1, `1`= 0)) %>%
  mutate(phq_06 = recode(phq_06, `4` = 3, `3` = 2, `2` = 1, `1`= 0)) %>%
  mutate(phq_07 = recode(phq_07, `4` = 3, `3` = 2, `2` = 1, `1`= 0)) %>%
  mutate(phq_08 = recode(phq_08, `4` = 3, `3` = 2, `2` = 1, `1`= 0)) %>%
  mutate(phq_09 = recode(phq_09, `4` = 3, `3` = 2, `2` = 1, `1`= 0)) %>%
  mutate(phq_10 = recode(phq_10, `4` = 3, `3` = 2, `2` = 1, `1`= 0)) 

phq <- df_transf[ , 54:62]

head(phq)

```

### Reversed Items

These are the original items and their reversed points. Replacing the first by the later then dropping the reversed
The only scale concerning anxiety/depression that has reversed items is the binary scale TMAS (reversed columns from 225 to 236). 

```{r}

#In case it's necessary to visualize all the cols iwth original reversed/pairs in a single vector you have it below commented out
#c(10, 215, 13, 216, 16, 217, 21, 218, 25, 219, 27, 220, 28, 221, 30, 222, 31, 223, 33, 224, 150, 225, 153, 226, 154, 227, 157, 228, 164, 229, 165, 230, 166, 231, 175, 232, 185, 233, 195, 234, 196, 235, 198, 236)

lv <- list(c(10, 215), c(13, 216), c(16, 217), c(21, 218), c(25, 219), c(27, 220), c(28, 221), c(30, 222), c(31, 223), c(33, 224), c(150, 225), c(153, 226), c(154, 227), c(157, 228), c(164, 229), c(165, 230), c(166, 231), c(175, 232), c(185, 233), c(195, 234), c(196, 235), c(198, 236))

for(i in lv){
# Replace the content by reverse item
df_transf[i[1]] <- df_transf[i[2]]}

df_transf <- df_transf[, - c(215:length(df_transf))]


```


Before saving the final version, it's necessary to remove certain items that are present in the DF but are not going to be relevant for the study.

```{r}

#Columns to delete
to_del <- c("dass_01", "dass_06", "dass_08", "dass_11", "dass_12", "dass_14", "dass_18", "phq_10")

df_transf <- df_transf[, -which(names(df_transf) %in% to_del)]

df_transf

```

## CSV

```{r}
write.csv(df_transf, 'data_cleaned_temp.csv', row.names = FALSE)
```

```{r}
d <- read.csv('data_cleaned_temp.csv')
colnames(d)
```


Ids = 1, Sociodem = 2:8, Pers_BFI2 = 9:23, Pers_hexaco = 24:33, Depr_cesd = 34:53, Depr_phq = 54:62, Depr_promis = 63:90, Depr_qids = 91:106, Depr_Ans_dass = 107:120, Depr_Ans_hads = 121:134, Ans_gad = 135:141, Ans_tmas = 142:191, Ans_sas = 192:206


```{r}
 
df_sums <- d[1] 
df_sums$sum_cesd <- rowSums(d[34:53])
df_sums$sum_phq <- rowSums(d[54:62])
df_sums$sum_promis <- rowSums(d[63:90])
df_sums$sum_qids <- rowSums(d[91:106])
df_sums$sum_dass <- rowSums(d[107:120])
df_sums$sum_hads <- rowSums(d[121:134])
df_sums$sum_gad <- rowSums(d[135:141])
df_sums$sum_tmas <- rowSums(d[142:191])
df_sums$sum_sas <- rowSums(d[192:206])

df_sums

```

